### 2020-09-23 paper/main.tex
adding paper

\documentclass{agujournal2019-navid}

\graphicspath{ {figures/} }
\usepackage{lineno,layouts,microtype}

% \linenumbers

\newcommand{\navidcomment}[1]{{\color{red} [#1]}}
\newcommand{\andycomment}[1]{{\color{Green} [#1]}}

%\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault} 
\usepackage{sansmath} 
\sansmath

\newcommand{\mathbfit}[1]{\textbf{\textit{\textsf{#1}}}}
\usepackage{amsfonts, amssymb, amsmath}
\usepackage[labelfont=bf]{caption}
% \usepackage{doi}

\usepackage{comment}

%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

%% Enter journal name below.
%% Choose from this list of Journals:
%
% JGR: Atmospheres
% JGR: Biogeosciences
% JGR: Earth Surface
% JGR: Oceans
% JGR: Planets
% JGR: Solid Earth
% JGR: Space Physics
% Global Biogeochemical Cycles
% Geophysical Research Letters
% Paleoceanography and Paleoclimatology
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resources Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science
% Geohealth
%
% ie, \journalname{Water Resources Research}

% \journalname{Geophysical Research Letters}

\usepackage{scalerel, stackengine}
\setstackEOL{\#}
\stackMath
\def\hatgap{2pt}
\def\subdown{-2pt}
\newcommand\reallywidehat[2][]{ \renewcommand\stackalignment{l} \stackon[\hatgap]{#2}{ \stretchto{
    \scalerel*[\widthof{$#2$}]{\kern-.6pt\bigwedge\kern-.6pt}
    {\rule[-\textheight/2]{1ex}{\textheight}}}
    {0.5ex}_{\smash{ \belowbaseline[\subdown]{\scriptstyle#1} }}
}}

%% MACROS

% Vector calculus 
  \newcommand{\p}		{\partial}
  \newcommand{\bnabla}	{\boldsymbol \nabla}
  \newcommand{\grad}	{\bnabla}
\renewcommand{\div}	    {\bnabla \bcdot}
  \newcommand{\bcdot}	{\boldsymbol \cdot}
  \newcommand{\lap}		{\triangle}

% Boldsymbols
\newcommand{\bu}		{\boldsymbol{u}}
\newcommand{\bx}		{\mathbfit x}
\newcommand{\bU}		{\mathbfit{U}}
\newcommand{\bX}		{\mathbfit{X}}
\newcommand{\bxh}		{\hspace{0.1em} \boldsymbol{\hat x}}
\newcommand{\byh}		{\hspace{0.1em}\boldsymbol{\hat y}}
\newcommand{\bzh}		{\hspace{0.1em}\boldsymbol{\hat z}}
\newcommand{\bnh}		{\hspace{0.1em}\boldsymbol{\hat n}}
\newcommand{\bxi}		{\ensuremath {\boldsymbol {\xi}}}

% Greek
\newcommand{\ep}		{\epsilon}
\newcommand{\om}		{\omega}
\newcommand{\kap}		{\kappa}
\newcommand{\sig}		{\sigma}
\newcommand{\gam}	  {\gamma}
\newcommand{\lam}		{\lambda}

% Romans
\newcommand{\ee}		{\mathrm{e}}
\newcommand{\ii}		{\mathrm{i}}
\newcommand{\dd}		{{\rm d}}
\newcommand{\id}		{{\, \rm d}}

% Misc
\newcommand{\Dt}[1]	    {\mathrm{D}_t #1}
\newcommand{\half}		{\tfrac{1}{2}}
\newcommand{\where}	    {\qquad \text{where} \qquad}
\newcommand{\andand}	{\qquad \text{and} \qquad}
\newcommand{\com}		{\, ,}
\newcommand{\per}		{\, .}
\newcommand{\defn}	    {\ensuremath{\stackrel{\mathrm{def}}{=}}}
\renewcommand{\equiv} {\ensuremath{\stackrel{\mathrm{def}}{=}}}
\newcommand{\av}[1]	    {\left \langle {#1} \right \rangle}
\newcommand{\beq}		{\begin{equation}}
\newcommand{\eeq}		{\end{equation}}
\newcommand{\Pa}		{\mathrm{N}\,\mathrm{m}^{-2}}
\newcommand{\rhom} {\rho_{\mathrm{m}}}
\newcommand{\ws} {\mathrm{WS}}
\newcommand{\tfs} {\mathrm{TFS}}
\newcommand{\ifs} {\mathrm{IFS}}
\newcommand{\bd} {\mathrm{BD}}
\newcommand{\hb} {h_{\mathrm{bot}}}
\newcommand{\pb} {p_{\mathrm{bot}}}

\hypersetup{
	breaklinks,
	colorlinks=true,
	linkcolor=Blue,
  urlcolor=Purple,
	citecolor=Purple,
%	allcolors=black,
	pdfauthor={N. C. Constantinou and A. McC. Hogg}
 }

\begin{document}
\justify
\title{Circumpolar variations in Southern Ocean eddy dynamics:\\An ensemble approach}

\authors{
Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{3}, William K. Dewar\affil{4},\\Navid C. Constantinou\affil{1}\quad and\quad Josu{\'e} Mart{\'i}nez Moreno\affil{1}
}

\affiliation{1}{Research School of Earth Sciences and ARC Centre of Excellence for Climate Extremes,\\ Australian National University, Australia}
\affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, IGE, Grenoble, France}
\affiliation{3}{Institut des Géosciences de l'Environnement, CNRS/Univ. Grenoble Alpes/G-INP/IRD, France}
\affiliation{3}{Florida State University, Tallahassee, FL, USA}

\correspondingauthor{Navid C. Constantinou}{navid.constantinou@anu.edu.au}

% \begin{keypoints}
% \item An isopycnal layered model, with a varying number of fluid layers, is used to assess relative importance of barotropic and baroclinic processes in the Southern Ocean.
% \item Both baroclinic and barotropic flows exhibit regimes in which mean zonal transport is insensitive to wind stress.
% \item Eddies actively shape the time-mean flow, irrespective of the instabilities from which they originate. 
% \end{keypoints}

\begin{abstract}
We study here this and that...

\noindent \textbf{Plain language summary} \\
\noindent In plain words, we do this and that...
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

\section{Introduction}

Southern Ocean eddies are important to the climate response - for compensation, saturation, etc.

Proxy for eddy strength is Transient KE (TKE), often called eddy KE. Define.

TKE responds to variations in wind stress forcing, but with a lag. Studied by many. This lag is relevant for eddy saturation and LFV.

Confusion about what this lag might be. It seems to be event- and region-dependent. Also, not clear whether it emerges from the noise in either model simulations or observations.

So, let’s reduce the noise with an ensemble approach. Look at both SO-wide and regional responses.

\section{Methods}

Model description (Thierry)

OCCIPUT strategy (Thierry)

Calculating geouv from SSH, removing trends, etc. (Sally)

Paragraph on TKE and filtering  to eliminate seasonal signal (Andy)

Paragraph on intrinsic-forced ratio and its limitations.

\section{Results}
Figure 1 - (a) TKE snapshot and (b) TKE climatology

Figure 2 - Entire Southern Ocean:(a,b) cherrypicked experiments TKE + lag; (c) ensemble mean TKE + lag

Figure 3 - 4 or 6 sectors TKE + lag

Figure 4 - interesting regions - again 4 or 6 of them, TKE + lags

Figure 5 - Ri ration plot, and other global features

\section{Discussion}
How do we interpret intrinsic variance ratio in this case?

What can we infer about real world?

Propose hypotheses for two timescales (do we need to test these at all?)

\section{Conclusions}
\begin{itemize}
    \item Intrinsic variance is large.
    \item  Forced component exists and has two timescales.
    \item Short timescale is local eddy response - mixed  barotropic/baroclinic?
    \item Long timescale requires topographic feedback.

\end{itemize}

\acknowledgments
We acknowledge NCI for everything they do for us.

\bibliography{basic_references}

\end{document}

### 2021-05-21 paper/main.tex
editing paper

@@
 
-\correspondingauthor{Navid C. Constantinou}{navid.constantinou@anu.edu.au}
+\correspondingauthor{Andrew McC. Hogg}{Andy.Hogg@anu.edu.au}
 
-% \begin{keypoints}
-% \item An isopycnal layered model, with a varying number of fluid layers, is used to assess relative importance of barotropic and baroclinic processes in the Southern Ocean.
-% \item Both baroclinic and barotropic flows exhibit regimes in which mean zonal transport is insensitive to wind stress.
-% \item Eddies actively shape the time-mean flow, irrespective of the instabilities from which they originate. 
-% \end{keypoints}
+\begin{keypoints}
+\item Variations in the Southern Ocean eddy field are dominated by intrinsic, rather than forced, processes.
+\item The forced component of the the variance is governed by the local wind stress input.
+\item The eddy field lags variations in wind stress, with two clear timescales emerging: one at 6-9 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
+\end{keypoints}
 
 \begin{abstract}
-We study here this and that...
+Circulation in the Southern Ocean is unique in global ocean.
+The strong wind stress forcing and buoyancy fluxes, in concert with the lack of continental boundaries, conspire to drive the Antarctic Circumpolar Current replete with an intense eddy field.
+The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
+The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.
+Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of the Southern Ocean eddy field.
+We find that intrinsic processes dominate the eddy field.
+Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescale -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
+These results suggest that understanding Southern Ocean eddy dynamics requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.
 
 \noindent \textbf{Plain language summary} \\
-\noindent In plain words, we do this and that...
+\noindent The Southern Ocean is the most turbulent region of the world's oceans.
+The variations in this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
+But it's hard to get information about these eddies, because they occur on small scales in a large ocean basin that is poorly observed.
+In addition, the observational record is quite short, which makes it more difficult to use these observations to study what controls variation in the eddy field.
+For this reason, we take an eddy-permitting ocean model, and run it 50 times with the same forcing (but a slightly different initial state).
+The chaotic nature of the turbulent ocean means that these models runs diverge into different states.
+We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external forcing that is common to all experiments (such as wind forcing).
+We conclude that the Southern Ocean eddy field is dominated by intrinsic chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence.
 \end{abstract}
@@
 \section{Results}
-Figure 1 - (a) TKE snapshot and (b) TKE climatology
+Figure 1 - (a) TKE snapshot and (b) TKE climatology and perhaps (c) ensemble spread in TKE.
 
@@
 
-Figure 5 - Ri ration plot, and other global features
+Figure 5 - Ri ratio plot, and other global features
 

### 2021-05-26 paper/main.tex
more paper updates
editing

@@
 \section{Results}
-Figure 1 - (a) TKE snapshot and (b) TKE climatology and perhaps (c) ensemble spread in TKE.
 
-Figure 2 - Entire Southern Ocean:(a,b) cherrypicked experiments TKE + lag; (c) ensemble mean TKE + lag
+The intensity of the Southern Ocean eddy field is not uniform.
+Snapshots of eddy kinetic energy (e.g.
+Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
+The same patterns are evident in the ensemble mean of EKE (Fig.~\ref{Fig:1}b), although the signal of individual eddies is not longer apparent.
+The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is generally weak south of 60$^\circ$S.
+The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry (REF), albeit at slightly lower intensity, as expected in an eddy-permitting model (e.g.
+Kiss et al.
+REF).
 
-Figure 3 - 4 or 6 sectors TKE + lag
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=\hsize]{Figure1}
+\caption{(a) EKE snapshot and (b) ensemble mean EKE  }
+\label{Fig:1}
+\end{center}
+\end{figure}
 
-Figure 4 - interesting regions - again 4 or 6 of them, TKE + lags
+For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean, and plot the timeseries of this quantity in thin grey lines in Fig.~\ref{Fig:2}(a). 
+This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of intrinsic variability in the Southern Ocean eddy field.
+Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the coherent, forced, component of eddy variability is revealed.
+Averaged over this region the fraction, $R_i$, of intrinsic variance is 0.69, confirming the visual impression that intrinsic processes are dominant here.
 
-Figure 5 - Ri ratio plot, and other global features
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\hsize]{Figure2}
+\caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S).
+(a) Spatially averaged EKE for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation for the ensemble mean (blue) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta/orange.}
+\label{Fig:2}
+\end{center}
+\end{figure}
+
+Although Southern Ocean EKE is strongly intrinsic, there remains a significant component of forced variability.
+Previous studies have suggested that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
+This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results.
+However, the time-lagged correlations between wind stress and EKE suggests that this relationship is complex. 
+The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
+On the other hand, ensemble member 4 (magenta line) has a clear an significant (??) correlation with a 7-month lag, while member 5 (orange line) is correlated weakly at 6 months, and strongly correlated at a 28-month lag.
+These isolated examples highlight how each ensemble member behaves differently, but the ensemble mean (blue line) includes a correlation at $\sim$6 months and a second clear peak at $\sim$30 months.
+Thus, there appear to be two distinct timescales of response of the Southern Ocean eddy field to wind stress.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\hsize]{Figure3}
+\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
+(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (3) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
+\label{Fig:3}
+\end{center}
+\end{figure}
+
+The ensemble of simulations shown here allow us to look in more detail at smaller regions of the Southern Ocean.
+Calculating the variability of EKE in a smaller region has the advantage of isolating different processes which may occur in differing regions (for example, stronger topographic steering in places with steep bathymetry).
+However, this advantage is partly offset by higher intrinsic variability in cases where the region of interest is so small that an individual eddy or event can have a large influence over the EKE timeseries.
+In balancing these competing issues, we look at the variability within regions that span 15-20$\circ$ in latitude and 30-40$^\circ$ in longitude, as shown in Figure \ref{Fig:3}(a).
+We analyse the EKE timeseries averaged over these boxes -- including individual member EKE, ensemble mean EKE and lagged correlations between local wind stress forcing and the ensemble mean EKE in Fig.
+\ref{Fig:3}(b-e).
+
+We first examine a region in the lee of Kerguelen Plateau in the Southeast Indian Ocean (cyan box in Fig.~\ref{Fig:3}a).
+This region is characterised by high-frequency ($\sim$1 year) variations in EKE, with a relatively large forced component (the intrinsic variance fraction $R_i = 0.51$ which is smaller than the Southern Ocean average; Fig.~\ref{Fig:3}b).
+The forced variation is clearly evident in the timeseries of from individual ensemble members; and this forced component is closely related to wind stress.
+The lag between wind stress variations and ensemble mean EKE is short ($\sim$ 6 months; Fig.~\ref{Fig:3}c) with a single peak in the lagged correlation.
+This region highlights a regime in which the eddy field responds rapidly to variations in the local wind stress.
+
+In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation is clearly different.
+Here, the intrinsic variance fraction is similar to the Southeast Indian Ocean ($R_i=0.56$) but the timescale of the variability is much longer and there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
+The peak in the lag correlation occurs at approximately 14 months in this region, and again has only a single clear peak.
+Thus, this region varies slowly and consistently to multi-year variations in wind stress.
+
+in the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is more dominated by intrinsic variance ($R_i=0.65$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3c,e), reinforcing the circumpolar variability of the EKE response to wind.
+
+Figure 5 -- showing that it is local wind forcing that matters
+
+Figure 6 - Ri ratio plot, and other global features
 

### 2021-06-06 paper/main.tex
adding intro

@@
 
-Southern Ocean eddies are important to the climate response - for compensation, saturation, etc.
+The Southern Ocean is unique in the global ocean; it is the one region without continents on its zonal boundaries, giving rise to the Antarctic Circumpolar Current (ACC) which flows eastward around the globe.
+The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
+The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification.
+However, the Southern Ocean is also poorly observed (compared with other ocean basins) and it's unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
 
-Proxy for eddy strength is Transient KE (TKE), often called eddy KE. Define.
+Another unique feature of the Southern Ocean is that it has a strong eddy field (Fu?).
+This strong eddy field has suggested to be important in the Southern Ocean's response to change.
+For example, the eddy saturation hypothesis (Hallberg, Hogg, Munday, constantinuo) suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
+A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation (Morrison).
+Therefore, the response of fine scale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.
 
-TKE responds to variations in wind stress forcing, but with a lag. Studied by many. This lag is relevant for eddy saturation and LFV.
+The strength of the Southern Ocean eddy field is usually characterised by extracting the kinetic energy of transient motions; referred to by oceanographers as eddy kinetic energy (EKE). 
+It is important to highlight that EKE includes all transient motion, not just coherent vortices (Martinez Moreno 2019), and thus care needs to be taken in interpreting this metric.
+Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
+Meredith \& Hogg (2006) found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
+Patara et al. 2016, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship is variable around the Southern Ocean.
+Idealised models over a wide range of parameter space (Sinha \& Abernathey) have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
+Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship, and the role of intrinsic variability, need to be clarified.
 
-Confusion about what this lag might be. It seems to be event- and region-dependent. Also, not clear whether it emerges from the noise in either model simulations or observations.
+On longer timescales it has also been proposed that EKE has increased over recent decades (Hogg et al. 2015, Martinez Moreno 2019),
+The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by Zhang et al. (2021).
+These authors used crossover data from satellite observations (as in Hogg et al. 2015) to better estimate the EKE on regional scales. 
+When fine graining these calculations it was found that only a couple of regions expressed a significant relationship between forcing and EKE.
+This suggests that previous characterisations of the response may have been dominated by a small number of regional events, and that at other times the intrinsic variance may dominate the signal.
 
-So, let’s reduce the noise with an ensemble approach. Look at both SO-wide and regional responses.
+Thus, despite the proposed importance of the Southern Ocean eddy field to ocean circulation, the nature of the EKE variability remains unclear.
+A primary complication is what can be inferred from an admittedly short satellite record; in particular, whether individual events can be attributed to forcing changes, or to intrinsic variability, or a combination of the two.
+In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in an ensemble of eddy-permitting  ocean models.
+We use the OCCIPUT ensemble (Penduff et al .), a 50-member ensemble of hindcast simulations.
+We examine both the intrinsic variance of the eddy field, and extract the ``forced'' (ensemble mean) component of the variability.
+This variability is examined on a circumpolar and regional basis, to better understand the regional differences and processes which contribute to the eddy field.
 
@@
 However, this advantage is partly offset by higher intrinsic variability in cases where the region of interest is so small that an individual eddy or event can have a large influence over the EKE timeseries.
-In balancing these competing issues, we look at the variability within regions that span 15-20$\circ$ in latitude and 30-40$^\circ$ in longitude, as shown in Figure \ref{Fig:3}(a).
+In balancing these competing issues, we look at the variability within regions that span 15-20$^\circ$ in latitude and 30-40$^\circ$ in longitude, as shown in Figure \ref{Fig:3}(a).
 We analyse the EKE timeseries averaged over these boxes -- including individual member EKE, ensemble mean EKE and lagged correlations between local wind stress forcing and the ensemble mean EKE in Fig.
@@
 
-in the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is more dominated by intrinsic variance ($R_i=0.65$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3c,e), reinforcing the circumpolar variability of the EKE response to wind.
+In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is more dominated by intrinsic variance ($R_i=0.65$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar variability of the EKE response to wind.
+Other regions (not shown) highlight different aspects of the response, with almost no correlation with wind forcing over the Southeast Pacific Ocean, and a long, $\sim30$-month response in the Southwest Indian Ocean with strong intrinsic variability.
+The circumpolar variation in both EKE response times and intrinsic variability suggests that the two-timescale response seen in Fig.
+\ref{Fig:2} may be created by different processes, which each dominate in different regions of the Southern Ocean.
 

### 2021-06-06 paper/main.tex
starting intro

@@
-\documentclass{agujournal2019-navid}
+\documentclass{agujournal2019}
 
@@
 
-% \linenumbers
+\usepackage{natbib}
+
+\linenumbers
 
@@
 
-% \journalname{Geophysical Research Letters}
-
-\usepackage{scalerel, stackengine}
-\setstackEOL{\#}
-\stackMath
-\def\hatgap{2pt}
-\def\subdown{-2pt}
-\newcommand\reallywidehat[2][]{ \renewcommand\stackalignment{l} \stackon[\hatgap]{#2}{ \stretchto{
-    \scalerel*[\widthof{$#2$}]{\kern-.6pt\bigwedge\kern-.6pt}
-    {\rule[-\textheight/2]{1ex}{\textheight}}}
-    {0.5ex}_{\smash{ \belowbaseline[\subdown]{\scriptstyle#1} }}
-}}
-
-%% MACROS
-
-% Vector calculus 
-  \newcommand{\p}		{\partial}
-  \newcommand{\bnabla}	{\boldsymbol \nabla}
-  \newcommand{\grad}	{\bnabla}
-\renewcommand{\div}	    {\bnabla \bcdot}
-  \newcommand{\bcdot}	{\boldsymbol \cdot}
-  \newcommand{\lap}		{\triangle}
-
-% Boldsymbols
-\newcommand{\bu}		{\boldsymbol{u}}
-\newcommand{\bx}		{\mathbfit x}
-\newcommand{\bU}		{\mathbfit{U}}
-\newcommand{\bX}		{\mathbfit{X}}
-\newcommand{\bxh}		{\hspace{0.1em} \boldsymbol{\hat x}}
-\newcommand{\byh}		{\hspace{0.1em}\boldsymbol{\hat y}}
-\newcommand{\bzh}		{\hspace{0.1em}\boldsymbol{\hat z}}
-\newcommand{\bnh}		{\hspace{0.1em}\boldsymbol{\hat n}}
-\newcommand{\bxi}		{\ensuremath {\boldsymbol {\xi}}}
-
-% Greek
-\newcommand{\ep}		{\epsilon}
-\newcommand{\om}		{\omega}
-\newcommand{\kap}		{\kappa}
-\newcommand{\sig}		{\sigma}
-\newcommand{\gam}	  {\gamma}
-\newcommand{\lam}		{\lambda}
-
-% Romans
-\newcommand{\ee}		{\mathrm{e}}
-\newcommand{\ii}		{\mathrm{i}}
-\newcommand{\dd}		{{\rm d}}
-\newcommand{\id}		{{\, \rm d}}
-
-% Misc
-\newcommand{\Dt}[1]	    {\mathrm{D}_t #1}
-\newcommand{\half}		{\tfrac{1}{2}}
-\newcommand{\where}	    {\qquad \text{where} \qquad}
-\newcommand{\andand}	{\qquad \text{and} \qquad}
-\newcommand{\com}		{\, ,}
-\newcommand{\per}		{\, .}
-\newcommand{\defn}	    {\ensuremath{\stackrel{\mathrm{def}}{=}}}
-\renewcommand{\equiv} {\ensuremath{\stackrel{\mathrm{def}}{=}}}
-\newcommand{\av}[1]	    {\left \langle {#1} \right \rangle}
-\newcommand{\beq}		{\begin{equation}}
-\newcommand{\eeq}		{\end{equation}}
-\newcommand{\Pa}		{\mathrm{N}\,\mathrm{m}^{-2}}
-\newcommand{\rhom} {\rho_{\mathrm{m}}}
-\newcommand{\ws} {\mathrm{WS}}
-\newcommand{\tfs} {\mathrm{TFS}}
-\newcommand{\ifs} {\mathrm{IFS}}
-\newcommand{\bd} {\mathrm{BD}}
-\newcommand{\hb} {h_{\mathrm{bot}}}
-\newcommand{\pb} {p_{\mathrm{bot}}}
-
-\hypersetup{
-	breaklinks,
-	colorlinks=true,
-	linkcolor=Blue,
-  urlcolor=Purple,
-	citecolor=Purple,
-%	allcolors=black,
-	pdfauthor={N. C. Constantinou and A. McC. Hogg}
- }
+\journalname{JGR: Oceans}
 
@@
 
-Model description (Thierry)
+\subsection{The OCCIPUT ensemble}
 
-OCCIPUT strategy (Thierry)
+The methodology employed in this study is derived from the probabilistic approach to ocean modelling outinlined by \citet{Bessieres2017}.
+We use output from the OCCIPUT (oceanic chaos – impacts, structure, predictability) ensemble of 50 eddy-permitting ocean model simulations, run in lock-step \citep{Leroux2018}.
+This ensemble is based on the DRAKKAR-ORCA025 \citep[e.g.][]{Barnier2006} implementation of the NEMO modelling system \citep{Madec2012}.
+The ensemble incorporates ocean-sea ice hindcast simulations for the period 1960-2015.
+The ensemble uses the DRAKKAR Forcing Set DFS5.2 (Dussin 2016) with  0.25$^\circ$ lateral resolution and 75 vertical levels.
 
@@
 In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is more dominated by intrinsic variance ($R_i=0.65$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar variability of the EKE response to wind.
-Other regions (not shown) highlight different aspects of the response, with almost no correlation with wind forcing over the Southeast Pacific Ocean, and a long, $\sim30$-month response in the Southwest Indian Ocean with strong intrinsic variability.
+Other regions (see Fig.
+\ref{Fig:4}) highlight different aspects of the response;  with almost no correlation with wind forcing over the Southwest Indian Ocean (the Agulhas meander region; Fig.
+\ref{Fig:4}b) or the Central South Pacific (Fig.
+\ref{Fig:4}d).
+In both of these regions, intrinsic variability dominates the signal.
+On the other hand, the Southeast Pacific (north of the main pathway of the ACC) shows a strong and coherent multi-year response to wind stress; albeit with a very weak EKE signal (one tenth the magnitude of the core of the ACC).
 The circumpolar variation in both EKE response times and intrinsic variability suggests that the two-timescale response seen in Fig.
 \ref{Fig:2} may be created by different processes, which each dominate in different regions of the Southern Ocean.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\hsize]{Figure4}
+\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
+(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southwest Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the South CentralPacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (3) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
+\label{Fig:4}
+\end{center}
+\end{figure}
 
@@
 
-\bibliography{basic_references}
+\bibliography{references}
 

### 2021-06-14 paper/main.tex
minor text updates

@@
 %\usepackage[T1]{fontenc}
-\renewcommand*\familydefault{\sfdefault} 
-\usepackage{sansmath} 
-\sansmath
+%\renewcommand*\familydefault{\sfdefault} 
+%\usepackage{sansmath} 
+%\sansmath
 
@@
 
-Calculating geouv from SSH, removing trends, etc. (Sally)
+\subsection{Calculating geouv from SSH, removing trends, etc. (Sally)}
 
-Paragraph on TKE and filtering  to eliminate seasonal signal (Andy)
+\subsection{TKE and filtering  to eliminate seasonal signal}
 
-Paragraph on intrinsic-forced ratio and its limitations.
+\subsection{Ratio of intrinsic to forced variance}
+
+Calculate the time-variance of the ensemble-mean EKE:
+$$\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2$$
+
+Take the difference from the ensemble mean for each member:
+$$E_i' = E_i - \langle E_i \rangle$$
+This allows us to accumulate the ensemble variance,
+$$\epsilon^2(t) = \frac{1}{N} \sum_{n=i}^N E_i'(t)^2$$
+indicating the spread of each member from the ensemble mean.
+
+Now calculate the ratio of intrinsic variance
+$$ R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}$$
 
@@
 
-For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean, and plot the timeseries of this quantity in thin grey lines in Fig.~\ref{Fig:2}(a). 
+For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean, and plot the deseasonalised EKE anomalies in thin grey lines in Fig.~\ref{Fig:2}(a). 
 This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of intrinsic variability in the Southern Ocean eddy field.
-Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the coherent, forced, component of eddy variability is revealed.
-Averaged over this region the fraction, $R_i$, of intrinsic variance is 0.69, confirming the visual impression that intrinsic processes are dominant here.
+Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
+Averaged over this region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes are dominant in the Southern Ocean eddy field.
 
@@
 \caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S).
-(a) Spatially averaged EKE for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation for the ensemble mean (blue) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta/orange.}
+(a) Spatially averaged EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta/orange.}
 \label{Fig:2}
@@
 The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
-On the other hand, ensemble member 4 (magenta line) has a clear an significant (??) correlation with a 7-month lag, while member 5 (orange line) is correlated weakly at 6 months, and strongly correlated at a 28-month lag.
-These isolated examples highlight how each ensemble member behaves differently, but the ensemble mean (blue line) includes a correlation at $\sim$6 months and a second clear peak at $\sim$30 months.
+On the other hand, ensemble member 5 (magenta line) has a clear (and significant; T-value = 5.5) correlation with a 4-month lag, while member 25 (orange line) is correlated weakly at 6 months, and significantly correlated (T-value = 4.2) at a 24-month lag.
+These isolated examples highlight how each ensemble member behaves differently, but the ensemble mean (red line) includes a significant correlation at $\sim$4 months and a second sifgnificant peak at $\sim$30 months.
 Thus, there appear to be two distinct timescales of response of the Southern Ocean eddy field to wind stress.
@@
 
-Figure 5 -- showing that it is local wind forcing that matters
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\hsize]{Figure5}
+\caption{ TBC}
+\label{Fig:5}
+\end{center}
+\end{figure}
 
-Figure 6 - Ri ratio plot, and other global features
+The correlations between local wind and the ensemble mean EKE shows that, where forced variability in Southern Ocean EKE occurs, it can be well-explained by variations in wind stress.
+However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
+The existence of multi-year lags between the wind and the EKE suggests that local winds may not be the only source of energy for eddy generation; in particular, it is possible that energy could be advected a considerable distance downstream during this lag period.
+To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}.
+To make this calculation, wind stress is first coarsened to a 2$^\circ \times $2$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with EKE at different lags.
+In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 7 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
+These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong correlations between wind stress at a given latitude; nonetheless, the maximum correlation between wind stress and EKE occurs within the EKE-averaging region.
+This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 7 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
+A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
+Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKE-averaging region.
+In the South Atlantic, the EKE is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d);
+Thus, these spatial maps demonstrate that, where strong forced variability in the EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
 
@@
 How do we interpret intrinsic variance ratio in this case?
+
+Figure 6 - Ri ratio plot, and other global features
 

### 2021-06-14 paper/main.tex
writing some text

@@
 \newcommand{\navidcomment}[1]{{\color{red} [#1]}}
-\newcommand{\andycomment}[1]{{\color{Green} [#1]}}
+\newcommand{\andycomment}[1]{{\color{blue} [#1]}}
 
@@
 
-\subsection{Calculating geouv from SSH, removing trends, etc. (Sally)}
+\andycomment{Thierry could add more if needed?}
 
-\subsection{TKE and filtering  to eliminate seasonal signal}
+\subsection{Estimating geostrophic eddy velocity}
+For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member) . 
+The sea level anomaly, $\eta_i'$ is calculated as the transient component of sea level, given by 
+\[ \eta_i' = \eta_i - \overline{\eta_i}\]
+where $\overline{\cdot}$ represents the temporal average over the simulation.
+The sea level anomaly is detrended, and then used to calculate the eddy velocity field.
+Surface eddy velocity in each ensemble member, $\mathbf{u}_i' = (u_i', v_i')$ is estimated from the detrended sea level anomaly via the geostrophic relation,
+\[u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y}; \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x}\]
+where $g$ is the acceleration due to gravity and $f$ is the local Coriolis parameter.
+Anomalous values of $\mathbf{u}_i'$ close to coastlines are removed.
+
+\andycomment{Sally to add details about SLA processing?}
+
+\subsection{Calculating eddy kinetic energy}
+The surface eddy kinetic energy for each ensemble member is calculated as 
+\[E_i = \frac{1}{2}(u_i'^2 + v_i'^2)\]
+and subsampled at monthly temporal resolution.
 

### 2021-06-14 paper/main.tex
adding discussion

@@
 \item Variations in the Southern Ocean eddy field are dominated by intrinsic, rather than forced, processes.
-\item The forced component of the the variance is governed by the local wind stress input.
-\item The eddy field lags variations in wind stress, with two clear timescales emerging: one at 6-9 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
+\item The forced component of the variance is significantly correlated with the local wind stress input.
+\item The eddy field lags variations in wind stress, with two clear timescales emerging: one at $\sim$6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
 \end{keypoints}
@@
 
-Another unique feature of the Southern Ocean is that it has a strong eddy field (Fu?).
+Another unique feature of the Southern Ocean is that it has a strong eddy field \citep{Fu2010}.
 This strong eddy field has suggested to be important in the Southern Ocean's response to change.
-For example, the eddy saturation hypothesis (Hallberg, Hogg, Munday, constantinuo) suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
-A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation (Morrison).
+For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
+A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
 Therefore, the response of fine scale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.
@@
 The strength of the Southern Ocean eddy field is usually characterised by extracting the kinetic energy of transient motions; referred to by oceanographers as eddy kinetic energy (EKE). 
-It is important to highlight that EKE includes all transient motion, not just coherent vortices (Martinez Moreno 2019), and thus care needs to be taken in interpreting this metric.
+It is important to highlight that EKE includes all transient motion, not just coherent vortices \citep{Martinez-Moreno2019}, and thus care needs to be taken in interpreting this metric.
 Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
-Meredith \& Hogg (2006) found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
-Patara et al. 2016, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship is variable around the Southern Ocean.
-Idealised models over a wide range of parameter space (Sinha \& Abernathey) have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
+\citet{Meredith2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
+\citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship is variable around the Southern Ocean.
+Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
 Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship, and the role of intrinsic variability, need to be clarified.
 
-On longer timescales it has also been proposed that EKE has increased over recent decades (Hogg et al. 2015, Martinez Moreno 2019),
-The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by Zhang et al. (2021).
-These authors used crossover data from satellite observations (as in Hogg et al. 2015) to better estimate the EKE on regional scales. 
-When fine graining these calculations it was found that only a couple of regions expressed a significant relationship between forcing and EKE.
-This suggests that previous characterisations of the response may have been dominated by a small number of regional events, and that at other times the intrinsic variance may dominate the signal.
+On longer timescales it has also been proposed that EKE has increased over recent decades \citep{Hogg2015, Martinez-Moreno2019}.
+The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by \citet{Zhang2021}, who used crossover data from satellite observations \citep[as in][]{Hogg2015} to better estimate the EKE on regional scales.
+When fine graining these calculations it was found that only a single region (30$^\circ$ in longitude) expressed a significant long-term trend in EKE.
+This finding  suggests that previous characterisations of the response may have been dominated by a small number of regional events, and that at other times the intrinsic variance may dominate the signal.
 
@@
 In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in an ensemble of eddy-permitting  ocean models.
-We use the OCCIPUT ensemble (Penduff et al .), a 50-member ensemble of hindcast simulations.
+We use the OCCIPUT ensemble \citep{Leroux2018}, a 50-member ensemble of hindcast simulations.
 We examine both the intrinsic variance of the eddy field, and extract the ``forced'' (ensemble mean) component of the variability.
@@
 
-\subsection{Calculating eddy kinetic energy}
 The surface eddy kinetic energy for each ensemble member is calculated as 
@@
 and subsampled at monthly temporal resolution.
+It is notable that $E_i$ contains a large component of seasonal variation (Mart\`inez-Moreno et al. 2021, submitted) which dominates the statistics.
+To look at the forced response, we therefore deseasonalise $E_i$, by removing the climatological mean for each month.
+We then proceed to compute ensemble statistics from this deseasonalised EKE.
 
-\subsection{Ratio of intrinsic to forced variance}
+\subsection{Ensemble eddy statistics}
 
-Calculate the time-variance of the ensemble-mean EKE:
-$$\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2$$
+The eddy kinetic energy can be averaged over the $N$ ensemble members to give the ensemble mean EKE, written as
+\[\langle E_i \rangle = \frac{1}{N} \sum_{i=1}^N E_i.\]
+The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is encapsulated by this ensemble mean quantity.
+On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
+\[E_i' = E_i - \langle E_i \rangle.\]
+Armed with these expressions we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
+\[\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2,\]
+which represents the variance of the forced eddy response.
+Analogously, the intrinsic variance emerges from the variance,
+$$\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i'(t)^2$$
+indicating the spread of each member from the ensemble mean.
+The fraction of intrinsic variance is then computed as the ratio of the intrinsic variance to the total variance,
+\[R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}.\]
+When $R_i$ approaches unity, the system is dominated by intrinsic variability, and at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.
 
-Take the difference from the ensemble mean for each member:
-$$E_i' = E_i - \langle E_i \rangle$$
-This allows us to accumulate the ensemble variance,
-$$\epsilon^2(t) = \frac{1}{N} \sum_{n=i}^N E_i'(t)^2$$
-indicating the spread of each member from the ensemble mean.
-
-Now calculate the ratio of intrinsic variance
-$$ R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}$$
+To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
+Thus, we look at the correlation coefficient, $r$, at a range of lags between the EKE and the wind stress $\tau$ (which is identical for all ensemble members).
+For each correlation we evaluate the statistical significance of the correlation \citep[following, e.g.][]{Santer2000}.
+We first calculate the effective sample size, $N_e$, where
+\[N_e \equiv N \frac{1-r_1 r_2}{1+r_1 r_2}\]
+where $N$ is the total number of samples (444 months for this timeseries), $r_1$ is the lag-1 autocorrelation for EKE and $r_2$ is the lag-2 autocorrelation for wind stress.
+We use the Students t-test to infer statistical significance (at the 95\%-level) based on this effective sample size, when
+\[T = \frac{r \sqrt{N_e}}{\sqrt{1-r^2}} > 2.\]
 
@@
 The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is generally weak south of 60$^\circ$S.
-The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry (REF), albeit at slightly lower intensity, as expected in an eddy-permitting model (e.g.
-Kiss et al.
-REF).
+The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.
 
@@
 \includegraphics[width=\hsize]{Figure1}
-\caption{(a) EKE snapshot and (b) ensemble mean EKE  }
+\caption{(a) Snapshot (5-day average) from a single ensemble member showing Southern Ocean EKE, $E_i$, and (b) tome-averagedensemble mean EKE, $\overline{\langle E_i\rangle}$.  }
 \label{Fig:1}
@@
 
-For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean, and plot the deseasonalised EKE anomalies in thin grey lines in Fig.~\ref{Fig:2}(a). 
+For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member in thin grey lines in Fig.~\ref{Fig:2}(a).
 This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of intrinsic variability in the Southern Ocean eddy field.
 Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
-Averaged over this region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes are dominant in the Southern Ocean eddy field.
+Averaged over this region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate eddy variability in the Southern Ocean eddy field.
 
@@
 \caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S).
-(a) Spatially averaged EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta/orange.}
+(a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
 \label{Fig:2}
@@
 
-Although Southern Ocean EKE is strongly intrinsic, there remains a significant component of forced variability.
+Although Southern Ocean EKE is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
 Previous studies have suggested that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
@@
 The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
-On the other hand, ensemble member 5 (magenta line) has a clear (and significant; T-value = 5.5) correlation with a 4-month lag, while member 25 (orange line) is correlated weakly at 6 months, and significantly correlated (T-value = 4.2) at a 24-month lag.
-These isolated examples highlight how each ensemble member behaves differently, but the ensemble mean (red line) includes a significant correlation at $\sim$4 months and a second sifgnificant peak at $\sim$30 months.
+On the other hand, ensemble member 5 (magenta line) has a clear (and significant; $T = 5.5$) correlation with a 4-month lag, while member 25 (orange line) is correlated weakly at 6 months, and significantly correlated ($T = 4.2$) at a 24-month lag.
+These isolated examples highlight the differing behaviour of each ensemble member. 
+The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
 Thus, there appear to be two distinct timescales of response of the Southern Ocean eddy field to wind stress.
@@
 The ensemble of simulations shown here allow us to look in more detail at smaller regions of the Southern Ocean.
-Calculating the variability of EKE in a smaller region has the advantage of isolating different processes which may occur in differing regions (for example, stronger topographic steering in places with steep bathymetry).
-However, this advantage is partly offset by higher intrinsic variability in cases where the region of interest is so small that an individual eddy or event can have a large influence over the EKE timeseries.
+Calculating the variability of EKE in a smaller region has the advantage of isolating the individual processes which may occur in differing regions (for example, stronger topographic steering in places with steep bathymetry).
+However, this advantage is partly offset by higher intrinsic variability;  in cases where the region of interest is sufficiently small that an individual eddy or event can have a large influence over the EKE timeseries.
 In balancing these competing issues, we look at the variability within regions that span 15-20$^\circ$ in latitude and 30-40$^\circ$ in longitude, as shown in Figure \ref{Fig:3}(a).
@@
 We first examine a region in the lee of Kerguelen Plateau in the Southeast Indian Ocean (cyan box in Fig.~\ref{Fig:3}a).
-This region is characterised by high-frequency ($\sim$1 year) variations in EKE, with a relatively large forced component (the intrinsic variance fraction $R_i = 0.51$ which is smaller than the Southern Ocean average; Fig.~\ref{Fig:3}b).
-The forced variation is clearly evident in the timeseries of from individual ensemble members; and this forced component is closely related to wind stress.
-The lag between wind stress variations and ensemble mean EKE is short ($\sim$ 6 months; Fig.~\ref{Fig:3}c) with a single peak in the lagged correlation.
+This region is characterised by high-frequency ($\sim$1 year) variations in EKE, with a relatively large forced component (the intrinsic variance fraction $R_i = 0.63$ which is smaller than the Southern Ocean average; Fig.~\ref{Fig:3}b).
+The forced variation is clearly evident in the timeseries of  individual ensemble members; and this forced component is related to wind stress.
+The lag between wind stress variations and ensemble mean EKE is short ($\sim$ 5 months; Fig.~\ref{Fig:3}c) with a single clear  and significant peak in the lagged correlation.
+There is a second, weaker but significant, correlation at 30 months lag.
 This region highlights a regime in which the eddy field responds rapidly to variations in the local wind stress.
@@
 In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation is clearly different.
-Here, the intrinsic variance fraction is similar to the Southeast Indian Ocean ($R_i=0.56$) but the timescale of the variability is much longer and there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
-The peak in the lag correlation occurs at approximately 14 months in this region, and again has only a single clear peak.
+Here, the intrinsic variance fraction is larger than the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
+The maximum values in the lag correlation occurs over a broad band from 9-24 months in this region, without a single clear peak.
 Thus, this region varies slowly and consistently to multi-year variations in wind stress.
 
-In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is more dominated by intrinsic variance ($R_i=0.65$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar variability of the EKE response to wind.
+In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is again dominated by intrinsic variance ($R_i=0.74$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar variability of the EKE response to wind.
 Other regions (see Fig.
-\ref{Fig:4}) highlight different aspects of the response;  with almost no correlation with wind forcing over the Southwest Indian Ocean (the Agulhas meander region; Fig.
-\ref{Fig:4}b) or the Central South Pacific (Fig.
-\ref{Fig:4}d).
-In both of these regions, intrinsic variability dominates the signal.
-On the other hand, the Southeast Pacific (north of the main pathway of the ACC) shows a strong and coherent multi-year response to wind stress; albeit with a very weak EKE signal (one tenth the magnitude of the core of the ACC).
+\ref{Fig:4}) highlight different aspects of the response;  with almost no correlation with wind forcing over the Central South Pacific ( Fig.
+\ref{Fig:4}b) or the Southwest Indian Ocean  (the Agulhas meander region; Fig.
+\ref{Fig:4}e).
+In both of these regions, intrinsic variability dominates the signal and correlations are weak and insignificant
+On the other hand, the Southeast Pacific (north of the main pathway of the ACC) shows a strong and coherent multi-year response to wind stress, with smaller intrinsic variance fraction and a peak lag at 30 months.
+It is notable that this region, which is north of the mean ACC pathway, has a weak EKE signal (one tenth the magnitude of the core of the ACC).
 The circumpolar variation in both EKE response times and intrinsic variability suggests that the two-timescale response seen in Fig.
@@
 \caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
-(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southwest Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the South CentralPacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (3) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
 The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
@@
 \includegraphics[width=\hsize]{Figure5}
-\caption{ TBC}
+\caption{The spatial correlation of wind stress with EKE in (a) the Southeast Indian Ocean at 5-month lag; (b) the Southeast Indian Ocean at 30-month lag; (c) the Southwest Pacific ocean at 15-month lag and (d) the South Atlantic Ocean at 17-month lag.}
 \label{Fig:5}
@@
 
-The correlations between local wind and the ensemble mean EKE shows that, where forced variability in Southern Ocean EKE occurs, it can be well-explained by variations in wind stress.
+The heterogeneity in correlations between local wind and the ensemble mean EKE shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
 However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
 The existence of multi-year lags between the wind and the EKE suggests that local winds may not be the only source of energy for eddy generation; in particular, it is possible that energy could be advected a considerable distance downstream during this lag period.
-To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}.
-To make this calculation, wind stress is first coarsened to a 2$^\circ \times $2$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with EKE at different lags.
-In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 7 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
+To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}).
+To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with EKE at different lags.
+In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
 These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong correlations between wind stress at a given latitude; nonetheless, the maximum correlation between wind stress and EKE occurs within the EKE-averaging region.
-This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 7 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
+This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
 A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
@@
 
-\section{Discussion}
-How do we interpret intrinsic variance ratio in this case?
+\section{Discussion and Conclusions}
+The simulations shown here advocate for a probabilistic approach to understanding the Southern Ocean eddy field.
+The 50-member ensemble of eddy-permitting ocean-sea ice model simulations investigated here demonstrate that inference about the EKE response of a single ensemble member to variable forcing is not robust, consistent with the inference of \citet{Zhang2021}.
+This point is clarified in Fig.~\ref{Fig:6} which shows a map of the intrinsic fraction of variance, $R_i$, from eddy statistics interpolated onto a coarse 5$^\circ \times$5$^\circ$ grid.
+Here, the intrinsic variance is close to unity over most of the band of elevated EKE in the Southern Ocean. 
+Subpanels (b) and (c) confirm the predominance of intrinsic eddy variability at this scale, highlighting that at small scales we can place little reliability on the results from an individual ensemble member.
 
-Figure 6 - Ri ratio plot, and other global features
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\hsize]{Figure6}
+\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  5$^\circ \times$5$^\circ$ grid; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes.}
+\label{Fig:6}
+\end{center}
+\end{figure}
 
-What can we infer about real world?
+When averaged over larger regions, the fraction of intrinsic variance can be smaller than shown in Fig.~\ref{Fig:6}.
+For example, in the Southeast Indian Ocean, in the lee of the Kerguelen Plateau, a strong and rapid response of EKE to the local wind stress can be observed.
+On the other hand, slower but significant responses in EKE are found in the Southwest Pacific Ocean, near Campbell Plateau (Fig.~\ref{Fig:3}).
+Both of these regions are locations where topography acts to sharpen and energise fronts.
+However, in many other regions, EKE variability appears to be almost entirely due to intrinsic processes.
+This heterogeneity, consistent with \citet{Patara2016}, acts to emphasise the differing flow regimes which are found in different parts of the Southern Ocean.
 
-Propose hypotheses for two timescales (do we need to test these at all?)
+Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and EKE: one at 4 months, and the other at $\sim$30 months.
+The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
+The slower timescale is similar to that proposed by \citet{Meredith2006}, based on the single large Southern Ocean wind event in 1999.
+ This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg2006}, in which a delayed amplification of the EKE response can occur through the topographic steering of currents away from the zonal direction, which decreases the stability of the current.
 
-\section{Conclusions}
-\begin{itemize}
-    \item Intrinsic variance is large.
-    \item  Forced component exists and has two timescales.
-    \item Short timescale is local eddy response - mixed  barotropic/baroclinic?
-    \item Long timescale requires topographic feedback.
-
-\end{itemize}
+The ensemble approach thus leads to the conclusion that eddy processes in the Southern Ocean include a large component of intrinsic variability, even when averaged over a large spatial area.
+This result argues for caution in interpreting observations of Southern Ocean eddies, which are necessarily based on a single, short realisation of the natural world.
+Given that eddies are critical for the Southern Ocean circulation, this result implies that predictability of the future Southern Ocean will be more difficult to realise than previously thought.
+It also highlights the difficulty faced in distinguishing the processes that govern eddy dynamics in this system, and point to more systematic eddy identification and modelling studies to better isolate these processes.
 
@@
 
+\andycomment{Thierry, please add OCCIPUT acknowledgements}
+
 \bibliography{references}

### 2021-06-16 paper/main.tex
minor edits to paper

@@
 The sea level anomaly, $\eta_i'$ is calculated as the transient component of sea level, given by 
-\[ \eta_i' = \eta_i - \overline{\eta_i}\]
+\begin{linenomath*}
+\begin{equation}
+\eta_i' = \eta_i - \overline{\eta_i}
+\end{equation}
+\end{linenomath*}
 where $\overline{\cdot}$ represents the temporal average over the simulation.
@@
 Surface eddy velocity in each ensemble member, $\mathbf{u}_i' = (u_i', v_i')$ is estimated from the detrended sea level anomaly via the geostrophic relation,
-\[u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y}; \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x}\]
+\begin{linenomath*}
+\begin{equation}
+u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y}; \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x}
+\end{equation}
+\end{linenomath*}
 where $g$ is the acceleration due to gravity and $f$ is the local Coriolis parameter.
@@
 The surface eddy kinetic energy for each ensemble member is calculated as 
-\[E_i = \frac{1}{2}(u_i'^2 + v_i'^2)\]
+\begin{linenomath*}
+\begin{equation}
+E_i = \frac{1}{2}(u_i'^2 + v_i'^2)
+\end{equation}
+\end{linenomath*}
 and subsampled at monthly temporal resolution.
@@
 The eddy kinetic energy can be averaged over the $N$ ensemble members to give the ensemble mean EKE, written as
-\[\langle E_i \rangle = \frac{1}{N} \sum_{i=1}^N E_i.\]
+\begin{linenomath*}
+\begin{equation}
+\langle E_i \rangle = \frac{1}{N} \sum_{i=1}^N E_i.
+\end{equation}
+\end{linenomath*}
 The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is encapsulated by this ensemble mean quantity.
 On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
-\[E_i' = E_i - \langle E_i \rangle.\]
+\begin{linenomath*}
+\begin{equation}
+E_i' = E_i - \langle E_i \rangle.
+\end{equation}
+\end{linenomath*}
 Armed with these expressions we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
-\[\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2,\]
+\begin{linenomath*}
+\begin{equation}
+\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2,
+\end{equation}
+\end{linenomath*}
 which represents the variance of the forced eddy response.
 Analogously, the intrinsic variance emerges from the variance,
-$$\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i'(t)^2$$
+\begin{linenomath*}
+\begin{equation}
+\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i'(t)^2
+\end{equation}
+\end{linenomath*}
 indicating the spread of each member from the ensemble mean.
 The fraction of intrinsic variance is then computed as the ratio of the intrinsic variance to the total variance,
-\[R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}.\]
+\begin{linenomath*}
+\begin{equation}
+R_i =  \frac{\overline{\epsilon^2}}{\overline{\epsilon^2} + \sigma^2_{\langle E \rangle}}.
+\end{equation}
+\end{linenomath*}
 When $R_i$ approaches unity, the system is dominated by intrinsic variability, and at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.
@@
 We first calculate the effective sample size, $N_e$, where
-\[N_e \equiv N \frac{1-r_1 r_2}{1+r_1 r_2}\]
+\begin{linenomath*}
+\begin{equation}
+N_e \equiv N \frac{1-r_1 r_2}{1+r_1 r_2}
+\end{equation}
+\end{linenomath*}
 where $N$ is the total number of samples (444 months for this timeseries), $r_1$ is the lag-1 autocorrelation for EKE and $r_2$ is the lag-2 autocorrelation for wind stress.
 We use the Students t-test to infer statistical significance (at the 95\%-level) based on this effective sample size, when
-\[T = \frac{r \sqrt{N_e}}{\sqrt{1-r^2}} > 2.\]
+\begin{linenomath*}
+\begin{equation}
+T = \frac{r \sqrt{N_e}}{\sqrt{1-r^2}} > 2.
+\end{equation}
+\end{linenomath*}
 
@@
 \acknowledgments
-We acknowledge NCI for everything they do for us.
-
+This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), which is supported by the Australian Government.
+AMH is gratefully to the support of 
 \andycomment{Thierry, please add OCCIPUT acknowledgements}

### 2021-06-16 paper/main.tex
minor edits

@@
 \begin{keypoints}
-\item Variations in the Southern Ocean eddy field are dominated by intrinsic, rather than forced, processes.
-\item The forced component of the variance is significantly correlated with the local wind stress input.
-\item The eddy field lags variations in wind stress, with two clear timescales emerging: one at $\sim$6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
+\item Variability in the Southern Ocean eddy field are dominated by intrinsic, rather than forced, processes.
+\item The forced component of the eddy kinetic energy variance is significantly correlated with the local wind stress input.
+\item The eddy field lags the wind stress, with two clear timescales emerging: one at $\sim$6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
 \end{keypoints}
@@
 \begin{abstract}
-Circulation in the Southern Ocean is unique in global ocean.
+Circulation in the Southern Ocean is unique.
 The strong wind stress forcing and buoyancy fluxes, in concert with the lack of continental boundaries, conspire to drive the Antarctic Circumpolar Current replete with an intense eddy field.
@@
 The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.
-Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of the Southern Ocean eddy field.
+Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
 We find that intrinsic processes dominate the eddy field.
-Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescale -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
+Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
 These results suggest that understanding Southern Ocean eddy dynamics requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.
@@
 \noindent \textbf{Plain language summary} \\
-\noindent The Southern Ocean is the most turbulent region of the world's oceans.
+\noindent The Southern Ocean is the most turbulent part of the world's oceans.
 The variations in this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
@@
 The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
-The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification.
+The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification (Morrison et al.
+Submitted) \citep{Rousselet2021}.
 However, the Southern Ocean is also poorly observed (compared with other ocean basins) and it's unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
@@
 
-The methodology employed in this study is derived from the probabilistic approach to ocean modelling outinlined by \citet{Bessieres2017}.
+The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
 We use output from the OCCIPUT (oceanic chaos – impacts, structure, predictability) ensemble of 50 eddy-permitting ocean model simulations, run in lock-step \citep{Leroux2018}.
@@
 The ensemble incorporates ocean-sea ice hindcast simulations for the period 1960-2015.
+We regard the first 20 years of this ensemble as being a spinup period, over which the ensemble members diverge, and analyse the period 1980-2015.
 The ensemble uses the DRAKKAR Forcing Set DFS5.2 (Dussin 2016) with  0.25$^\circ$ lateral resolution and 75 vertical levels.
 
-\andycomment{Thierry could add more if needed?}
+\andycomment{Thierry could add more or fix errors if needed?}
 
@@
 For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member) . 
-The sea level anomaly, $\eta_i'$ is calculated as the transient component of sea level, given by 
+The sea level anomaly, $\eta_i'$, is calculated as the transient component of sea level, given by 
 \begin{linenomath*}
@@
 To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
-Thus, we look at the correlation coefficient, $r$, at a range of lags between the EKE and the wind stress $\tau$ (which is identical for all ensemble members).
+Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $\tau$ (which is identical for all ensemble members) and EKE.
 For each correlation we evaluate the statistical significance of the correlation \citep[following, e.g.][]{Santer2000}.
@@
 \end{linenomath*}
+Lagged correlation estimates indicate when this significance test is satisfied.
 
@@
 \includegraphics[width=\hsize]{Figure1}
-\caption{(a) Snapshot (5-day average) from a single ensemble member showing Southern Ocean EKE, $E_i$, and (b) tome-averagedensemble mean EKE, $\overline{\langle E_i\rangle}$.  }
+\caption{(a) Snapshot (5-day average) from a single ensemble member showing Southern Ocean EKE, $E_i$, and (b) time-averaged ensemble mean EKE, $\overline{\langle E_i\rangle}$.  }
 \label{Fig:1}
@@
 \caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
-(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (3) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (c) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
 The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
@@
 There is a second, weaker but significant, correlation at 30 months lag.
-This region highlights a regime in which the eddy field responds rapidly to variations in the local wind stress.
+This region highlights a regime in which the eddy field primarily responds rapidly to variations in the local wind stress.
 
@@
 \ref{Fig:4}e).
-In both of these regions, intrinsic variability dominates the signal and correlations are weak and insignificant
+In both of these regions, intrinsic variability dominates the signal and correlations are weak and insignificant. 
 On the other hand, the Southeast Pacific (north of the main pathway of the ACC) shows a strong and coherent multi-year response to wind stress, with smaller intrinsic variance fraction and a peak lag at 30 months.
@@
 In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
-These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong correlations between wind stress at a given latitude; nonetheless, the maximum correlation between wind stress and EKE occurs within the EKE-averaging region.
+These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and EKE occurs within the EKE-averaging region.
 This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
@@
 Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKE-averaging region.
-In the South Atlantic, the EKE is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d);
+In the South Atlantic, the EKE is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
 Thus, these spatial maps demonstrate that, where strong forced variability in the EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
@@
 The simulations shown here advocate for a probabilistic approach to understanding the Southern Ocean eddy field.
-The 50-member ensemble of eddy-permitting ocean-sea ice model simulations investigated here demonstrate that inference about the EKE response of a single ensemble member to variable forcing is not robust, consistent with the inference of \citet{Zhang2021}.
+The 50-member ensemble of eddy-permitting ocean-sea ice model simulations investigated here demonstrate that inference about the EKE response of a single ensemble member to variable forcing in a localised region is not robust, consistent with the inference of \citet{Zhang2021}.
 This point is clarified in Fig.~\ref{Fig:6} which shows a map of the intrinsic fraction of variance, $R_i$, from eddy statistics interpolated onto a coarse 5$^\circ \times$5$^\circ$ grid.
@@
 However, in many other regions, EKE variability appears to be almost entirely due to intrinsic processes.
-This heterogeneity, consistent with \citet{Patara2016}, acts to emphasise the differing flow regimes which are found in different parts of the Southern Ocean.
+This heterogeneity, consistent with the findings of \citet{Patara2016}, acts to emphasise the differing flow regimes which are found in different parts of the Southern Ocean.
 
@@
 This result argues for caution in interpreting observations of Southern Ocean eddies, which are necessarily based on a single, short realisation of the natural world.
-Given that eddies are critical for the Southern Ocean circulation, this result implies that predictability of the future Southern Ocean will be more difficult to realise than previously thought.
+Given that eddies are critical for the Southern Ocean circulation, this result implies that predictability of the future Southern Ocean may be weaker than previously thought.
 It also highlights the difficulty faced in distinguishing the processes that govern eddy dynamics in this system, and point to more systematic eddy identification and modelling studies to better isolate these processes.
@@
 This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), which is supported by the Australian Government.
-AMH is gratefully to the support of 
+AMH is gratefully to the MEOM team at ICE, Universit{\'e} Grenoble Alpes, who supported his sabbatical and which led to this work.
+
 \andycomment{Thierry, please add OCCIPUT acknowledgements}

### 2021-06-17 paper/main.tex
adds bibliography

@@
 \usepackage[labelfont=bf]{caption}
-% \usepackage{doi}
+
+\hypersetup{
+	breaklinks,
+	colorlinks=true,
+	linkcolor=Blue,
+  urlcolor=Purple,
+	citecolor=Purple,
+%	allcolors=black,
+ }
+
+ \usepackage{doi}
 
@@
 \justify
-\title{Circumpolar variations in Southern Ocean eddy dynamics:\\An ensemble approach}
+\title{Circumpolar variations in Southern Ocean eddy dynamics: insights from an ensemble modelling approach}
 
@@
 
-\affiliation{1}{Research School of Earth Sciences and ARC Centre of Excellence for Climate Extremes,\\ Australian National University, Australia}
-\affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, IGE, Grenoble, France}
+\affiliation{1}{Research School of Earth Sciences and ARC Centre of Excellence for Climate Extremes,\\ Australian National University, Canberra, Australia}
+\affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, Institut des G{\'e}osciences de l'Environnement (IGE), Grenoble, France}
 \affiliation{3}{Institut des Géosciences de l'Environnement, CNRS/Univ. Grenoble Alpes/G-INP/IRD, France}
@@
 The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
-The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.
+The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.\footnote{{\color{red}Thierry: I agree, but some studies (e.g.
+Colin de Verdiere \& Huck 1999, Huck et al 2015) have mentioned that non-eddying ocean models can also produce (a small amount of) intrinsic variability via large-scale baroclinic instability.
+Need to mention?}}
 Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
@@
 Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
-These results suggest that understanding Southern Ocean eddy dynamics requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.
+These results suggest that understanding Southern Ocean eddy dynamics and its larger-scale impacts requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.
 
@@
 The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
-The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification (Morrison et al.
-Submitted) \citep{Rousselet2021}.
+The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2021}.
 However, the Southern Ocean is also poorly observed (compared with other ocean basins) and it's unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
@@
 This strong eddy field has suggested to be important in the Southern Ocean's response to change.
-For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
+For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
 A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
@@
 Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
-\citet{Meredith2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
+\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
 \citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship is variable around the Southern Ocean.
@@
 and subsampled at monthly temporal resolution.
-It is notable that $E_i$ contains a large component of seasonal variation (Mart\`inez-Moreno et al. 2021, submitted) which dominates the statistics.
+It is notable that $E_i$ contains a large component of seasonal variation \citep{Martinez-Moreno2021} which dominates the statistics.
 To look at the forced response, we therefore deseasonalise $E_i$, by removing the climatological mean for each month.
@@
 The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
-The slower timescale is similar to that proposed by \citet{Meredith2006}, based on the single large Southern Ocean wind event in 1999.
- This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg2006}, in which a delayed amplification of the EKE response can occur through the topographic steering of currents away from the zonal direction, which decreases the stability of the current.
+The slower timescale is similar to that proposed by \citet{Meredith-Hogg-2006}, based on the single large Southern Ocean wind event in 1999.
+This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg-Blundell-2006}, in which a delayed amplification of the EKE response can occur through the topographic steering of currents away from the zonal direction, which decreases the stability of the current.
 

### 2021-06-18 paper/main.tex

@@
 For this reason, we take an eddy-permitting ocean model, and run it 50 times with the same forcing (but a slightly different initial state).
-The chaotic nature of the turbulent ocean means that these models runs diverge into different states.
+The chaotic nature of the turbulent ocean means that these model runs exhibit different evolutions.
 We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external forcing that is common to all experiments (such as wind forcing).
@@
 \end{abstract}
+
+{\color{red}General Remarks by Thierry:
+
+\begin{itemize}
+	\item
+	Adopting the word intrinsic to name fluctuations around the ensemble mean is 100\% OK.
+But these fluctuations are also chaotic (in a broad sense), which implies that they limit predictability (as stated in the conclusion) and question the attribution of observed/simulated events to atmospheric drivers.
+In other words, the chaotic behavior of this variability is perhaps more important than its intrinsic origin, since it raises more concrete issues.
+This could maybe be stated more directly (?)
+
+	\item 
+	The fact that high-freq eddy variability is random/chaotic is well-known, and one of the main messages of the paper is that this character remains strong (and even dominant) over large regions and at long timescales (interannual).
+I suggest to insist a bit more on this (abstract, conclusion), which confirms our previous results on other variables (e.g.
+Leroux et al 2018, Serazin et al 2017, etc) : eddy chaos inversely cascades toward larger/longer scales and affects climate-relevant features (see Serazin et al 2018).
+
+\end{itemize}
+}
 
@@
 The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2021}.
-However, the Southern Ocean is also poorly observed (compared with other ocean basins) and it's unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
+However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
 
 Another unique feature of the Southern Ocean is that it has a strong eddy field \citep{Fu2010}.
-This strong eddy field has suggested to be important in the Southern Ocean's response to change.
+This strong eddy field has been suggested to be important in the Southern Ocean's response to change.
 For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
@@
 Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
-Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship, and the role of intrinsic variability, need to be clarified.
+Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship, and the role of intrinsic variability, need to be clarified.\footnote{{\color{red}Thierry: the notion of intrinsic variability could be introduced a bit more before this, explaining for instance that it emerges frrom oceanic non-linearities under constant or seasonal forcing and persists under variable forcing (Leroux et al 2018), it has a random phase (``chaotic'' character), it mostly emerges at mesoscale and can cascade toward interannual to decadal time scales and O(1000km) space scales (Serazin et al 2018).}}
 
@@
 A primary complication is what can be inferred from an admittedly short satellite record; in particular, whether individual events can be attributed to forcing changes, or to intrinsic variability, or a combination of the two.
-In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in an ensemble of eddy-permitting  ocean models.
-We use the OCCIPUT ensemble \citep{Leroux2018}, a 50-member ensemble of hindcast simulations.
+In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in an ensemble of eddy-permitting ocean simulations.
+We use the OCCIPUT ensemmble of global ocean/sea-ice hindcast simulations \citep{Penduff-etal-2014, Leroux2018}, a 50-member ensemble of hindcast simulations.
 We examine both the intrinsic variance of the eddy field, and extract the ``forced'' (ensemble mean) component of the variability.
@@
 The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
-We use output from the OCCIPUT (oceanic chaos – impacts, structure, predictability) ensemble of 50 eddy-permitting ocean model simulations, run in lock-step \citep{Leroux2018}.
-This ensemble is based on the DRAKKAR-ORCA025 \citep[e.g.][]{Barnier2006} implementation of the NEMO modelling system \citep{Madec2012}.
-The ensemble incorporates ocean-sea ice hindcast simulations for the period 1960-2015.
-We regard the first 20 years of this ensemble as being a spinup period, over which the ensemble members diverge, and analyse the period 1980-2015.
-The ensemble uses the DRAKKAR Forcing Set DFS5.2 (Dussin 2016) with  0.25$^\circ$ lateral resolution and 75 vertical levels.
-
-\andycomment{Thierry could add more or fix errors if needed?}
+We use output from the OCCIPUT (OceaniC Chaos – ImPacts, strUcture, predicTability) ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}.
+The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels.
+We employ the probabilistic ocean modelling approach outlined by \citet{Bessieres2017}: \emph{(i)}~the 50 ensemble members are initialized in 1960 from a one-member 21-year spinup; \emph{(ii)}~the ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} during one year in 1960, which is shut off afterwards; \emph{(iii)}~the 50 ensemble members are driven between 1960 and 2015 by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}); the wind stress is computed without ocean current feedbacks, hence ensuring that the same momentum fluxes are applied to all members.
+We focus our analyses on the period 1980-2015, thus yielding an effective spinup duration of 41 years in each member.
 
@@
 The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is encapsulated by this ensemble mean quantity.
-On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
+On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,\footnote{{\color{red}Thierry: instead of using the prime exponent (used for temporal anomalies), I suggest using e.g.
+a star (*) exponent for ensemble anomalies.}}
 \begin{linenomath*}
@@
 \end{linenomath*}
-Armed with these expressions we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
+With these expressions in hand, we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
 \begin{linenomath*}
@@
 Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
-The same patterns are evident in the ensemble mean of EKE (Fig.~\ref{Fig:1}b), although the signal of individual eddies is not longer apparent.
+The same patterns are evident in the ensemble and temporal mean of the EKE (Fig.~\ref{Fig:1}b), although the signal of individual eddies is not longer apparent.
 The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is generally weak south of 60$^\circ$S.
@@
 
-Although Southern Ocean EKE is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
+Although Southern Ocean EKE variability is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
 Previous studies have suggested that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
@@
 In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation is clearly different.
-Here, the intrinsic variance fraction is larger than the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
+Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
 The maximum values in the lag correlation occurs over a broad band from 9-24 months in this region, without a single clear peak.
-Thus, this region varies slowly and consistently to multi-year variations in wind stress.
+Thus, this region varies slowly and consistently to interannual variations in wind stress.
 
@@
 
-The heterogeneity in correlations between local wind and the ensemble mean EKE shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
+The heterogeneity in correlations between local wind and the ensemble-mean EKE ($\langle\textrm{EKE}\rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
 However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
@@
 To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}).
-To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with EKE at different lags.
+To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with ensemble-mean EKE at different lags.
 In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
-These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and EKE occurs within the EKE-averaging region.
-This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
+These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle\textrm{EKE}\rangle$ occurs within the $\langle\textrm{EKE}\rangle$)-averaging region.
+This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the $\langle\textrm{EKE}\rangle$-averaging region is not stronger than within the $\langle\textrm{EKE}\rangle$)-averaging region.
 A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
-Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKE-averaging region.
-In the South Atlantic, the EKE is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
-Thus, these spatial maps demonstrate that, where strong forced variability in the EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
+Importantly, there is no suggestion of a strong correlation with wind stress upstream of the $\langle\textrm{EKE}\rangle$-averaging region.
+In the South Atlantic, the $\langle\textrm{EKE}\rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
+Thus, these spatial maps demonstrate that, where strong forced variability in the $\langle\textrm{EKE}\rangle$ exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
+
+{\color{red}Navid: Thierry, did I make all the appropriate changes EKE $\to$ $\langle\textrm{EKE}\rangle$ correctly?}
 
@@
 \includegraphics[width=\hsize]{Figure6}
-\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  5$^\circ \times$5$^\circ$ grid; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes.}
+\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  5$^\circ \times$5$^\circ$ grid; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes.
+{\color{red}(Thierry: How about adding to this figure the same 3 maps for the interannual EKE variability alone?
+This would explicitly show that intrinsic signals remain strong even at low-frequencies: this can be explicitly stated in the text.)}}
 \label{Fig:6}
@@
 
-The ensemble approach thus leads to the conclusion that eddy processes in the Southern Ocean include a large component of intrinsic variability, even when averaged over a large spatial area.
+The ensemble approach thus leads to the conclusion that eddy processes in the Southern Ocean include a large component of intrinsic variability, even when averaged over a large spatial area and up to interannual time scales.
 This result argues for caution in interpreting observations of Southern Ocean eddies, which are necessarily based on a single, short realisation of the natural world.
@@
 AMH is gratefully to the MEOM team at ICE, Universit{\'e} Grenoble Alpes, who supported his sabbatical and which led to this work.
-
-\andycomment{Thierry, please add OCCIPUT acknowledgements}
+The results of this research have been achieved using the PRACE Research Infrastructure resource CURIE based in France at TGCC.
+This work is a contribution to the OCCIPUT and PIRATE projects.
+OCCIPUT has been funded by ANR through contract ANR-13-BS06-0007-01.
+PIRATE has been funded by CNES through the Ocean Surface Topography Science Team (OST-ST).
+{\color{red}The model output used in this study can be downloaded from the Zenodo repository at doi:XXX.XXX.XXX.
+The full OCCIPUT model dataset is available on request (\href{mailto:Thierry.Penduff@cnrs.fr}{Thierry.Penduff@cnrs.fr}).}
 

### 2021-09-27 paper/main.tex
fix Sally affiliation
don't enforce bibtex
adds Sally's remakrs + cite NCC paper + punctuate all eqs

@@
+% !TEX program = pdflatex
+% !TEX encoding = UTF-8 Unicode
+
 \documentclass{agujournal2019}
@@
 \authors{
-Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{3}, William K. Dewar\affil{4},\\Navid C. Constantinou\affil{1}\quad and\quad Josu{\'e} Mart{\'i}nez Moreno\affil{1}
+Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez Moreno\affil{1}
 }
@@
 \affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, Institut des G{\'e}osciences de l'Environnement (IGE), Grenoble, France}
-\affiliation{3}{Institut des Géosciences de l'Environnement, CNRS/Univ. Grenoble Alpes/G-INP/IRD, France}
 \affiliation{3}{Florida State University, Tallahassee, FL, USA}
@@
 Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
-Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship, and the role of intrinsic variability, need to be clarified.\footnote{{\color{red}Thierry: the notion of intrinsic variability could be introduced a bit more before this, explaining for instance that it emerges frrom oceanic non-linearities under constant or seasonal forcing and persists under variable forcing (Leroux et al 2018), it has a random phase (``chaotic'' character), it mostly emerges at mesoscale and can cascade toward interannual to decadal time scales and O(1000km) space scales (Serazin et al 2018).}}
+Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship, and the role of intrinsic variability, need to be clarified.\footnote{{\color{red}Thierry: the notion of intrinsic variability could be introduced a bit more before this, explaining for instance that it emerges frrom oceanic non-linearities under constant or seasonal forcing and persists under variable forcing \citep{Leroux2018}, it has a random phase (``chaotic'' character), it mostly emerges at mesoscale and can cascade toward interannual to decadal time scales and O(1000$\,$km) space scales \cite{Serazin-etal-2018}.}}
 
-On longer timescales it has also been proposed that EKE has increased over recent decades \citep{Hogg2015, Martinez-Moreno2019}.
+On longer timescales it has also been proposed that EKE has increased over recent decades \citep{Hogg2015, Martinez-Moreno2019, Martinez-Moreno2021-ncc}.
 The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by \citet{Zhang2021}, who used crossover data from satellite observations \citep[as in][]{Hogg2015} to better estimate the EKE on regional scales.
@@
 In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in an ensemble of eddy-permitting ocean simulations.
-We use the OCCIPUT ensemmble of global ocean/sea-ice hindcast simulations \citep{Penduff-etal-2014, Leroux2018}, a 50-member ensemble of hindcast simulations.
+We use the OCCIPUT ensemble of global ocean/sea-ice hindcast simulations \citep{Penduff-etal-2014, Leroux2018}, a 50-member ensemble of hindcast simulations\footnote{{\color{blue}Sally: The definition of OCCIPUT perhaps need to be moved up here from the paragraph below?}}.
 We examine both the intrinsic variance of the eddy field, and extract the ``forced'' (ensemble mean) component of the variability.
@@
 The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
-We use output from the OCCIPUT (OceaniC Chaos – ImPacts, strUcture, predicTability) ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}.
+We use output from the OCCIPUT (OceaniC Chaos – ImPacts, strUcture, predicTability) ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} \footnote{{\color{blue}Sally: I think there's a problem in the bibtex file here: the citation seems to be coming up as Bernard instead of Barnier}}of the NEMO modelling system \citep{Madec2012}.
 The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels.
@@
 For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member) .
+{\color{blue} Sally: For each ensemble member, the member's global mean sea level anomaly is subtracted from all grid points at every time step to correct for spurious terms introduced by the use of the Boussinesq approximation \citep{Greatbatch1994}.
+The model drift, which is potentially nonlinear, is then corrected for by detrending using a LOWESS filter \citep{Cleveland1979} in combination with a 5th-order spline; full details of this preprocessing may be found in \citep{Close2020}.}
+
 The sea level anomaly, $\eta_i'$, is calculated as the transient component of sea level, given by 
@@
 \begin{equation}
-\eta_i' = \eta_i - \overline{\eta_i}
+\eta_i' = \eta_i - \overline{\eta_i},
 \end{equation}
 \end{linenomath*}
-where $\overline{\cdot}$ represents the temporal average over the simulation.
+where $\overline{\cdot}$ represents the temporal average\footnote{{\color{blue}Sally: see above: instead of the temporal average it's the nonlinear trend that's removed}} over the simulation.
 The sea level anomaly is detrended, and then used to calculate the eddy velocity field.
@@
 \begin{equation}
-u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y}; \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x}
+u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y} \quad \text{and} \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x},
 \end{equation}
@@
 \begin{equation}
-E_i = \frac{1}{2}(u_i'^2 + v_i'^2)
+E_i = \frac{1}{2}(u_i'^2 + v_i'^2),
 \end{equation}
@@
 \begin{equation}
-\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i'(t)^2
+\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i'(t)^2,
 \end{equation}
@@
 \begin{equation}
-N_e \equiv N \frac{1-r_1 r_2}{1+r_1 r_2}
+N_e \equiv N \frac{1-r_1 r_2}{1+r_1 r_2},
 \end{equation}
@@
 \includegraphics[width=\hsize]{Figure1}
-\caption{(a) Snapshot (5-day average) from a single ensemble member showing Southern Ocean EKE, $E_i$, and (b) time-averaged ensemble mean EKE, $\overline{\langle E_i\rangle}$.  }
+\caption{(a) Snapshot (5-day average) from a single ensemble member showing Southern Ocean EKE, $E_i$, and (b) time-averaged ensemble mean EKE, $\overline{\langle E_i\rangle}$.}
 \label{Fig:1}

### 2021-12-13 paper/main.tex
minor updates

--- 2021-06-17 paper/main.tex
@@
 \usepackage[labelfont=bf]{caption}
-
-\hypersetup{
-	breaklinks,
-	colorlinks=true,
-	linkcolor=Blue,
-  urlcolor=Purple,
-	citecolor=Purple,
-%	allcolors=black,
- }
-
- \usepackage{doi}
+% \usepackage{doi}
 
@@
 \justify
-\title{Circumpolar variations in Southern Ocean eddy dynamics: insights from an ensemble modelling approach}
+\title{Circumpolar variations in Southern Ocean eddy dynamics: An ensemble approach}
 
 \authors{
-Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{3}, William K. Dewar\affil{4},\\Navid C. Constantinou\affil{1}\quad and\quad Josu{\'e} Mart{\'i}nez Moreno\affil{1}
+Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{3,4}, William K. Dewar\affil{3,5},\\Navid C. Constantinou\affil{1}\quad and\quad Josu{\'e} Mart{\'i}nez Moreno\affil{1}
 }
 
-\affiliation{1}{Research School of Earth Sciences and ARC Centre of Excellence for Climate Extremes,\\ Australian National University, Canberra, Australia}
-\affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, Institut des G{\'e}osciences de l'Environnement (IGE), Grenoble, France}
+\affiliation{1}{Research School of Earth Sciences and ARC Centre of Excellence for Climate Extremes,\\ Australian National University, Australia}
+\affiliation{2}{Universit{\'e} Grenoble Alpes, CNRS, IRD, Grenoble-INP, IGE, Grenoble, France}
 \affiliation{3}{Institut des Géosciences de l'Environnement, CNRS/Univ. Grenoble Alpes/G-INP/IRD, France}
-\affiliation{3}{Florida State University, Tallahassee, FL, USA}
+\affiliation{4}{University of Brest \andycomment{?}, France}
+\affiliation{5}{Florida State University, Tallahassee, FL, USA}
 
@@
 The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
-The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.\footnote{{\color{red}Thierry: I agree, but some studies (e.g.
-Colin de Verdiere \& Huck 1999, Huck et al 2015) have mentioned that non-eddying ocean models can also produce (a small amount of) intrinsic variability via large-scale baroclinic instability.
-Need to mention?}}
+The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.
 Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
@@
 Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
-These results suggest that understanding Southern Ocean eddy dynamics and its larger-scale impacts requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.
+These results suggest that understanding Southern Ocean eddy dynamics requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.
 
@@
 The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
-The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2021}.
+The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification (Morrison et al.
+Submitted) \citep{Rousselet2021}.
 However, the Southern Ocean is also poorly observed (compared with other ocean basins) and it's unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
@@
 This strong eddy field has suggested to be important in the Southern Ocean's response to change.
-For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
+For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
 A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
@@
 Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
-\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
+\citet{Meredith2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
 \citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship is variable around the Southern Ocean.
@@
 and subsampled at monthly temporal resolution.
-It is notable that $E_i$ contains a large component of seasonal variation \citep{Martinez-Moreno2021} which dominates the statistics.
+It is notable that $E_i$ contains a large component of seasonal variation (Mart\`inez-Moreno et al. 2021, submitted) which dominates the statistics.
 To look at the forced response, we therefore deseasonalise $E_i$, by removing the climatological mean for each month.
@@
 The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
-The slower timescale is similar to that proposed by \citet{Meredith-Hogg-2006}, based on the single large Southern Ocean wind event in 1999.
-This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg-Blundell-2006}, in which a delayed amplification of the EKE response can occur through the topographic steering of currents away from the zonal direction, which decreases the stability of the current.
+The slower timescale is similar to that proposed by \citet{Meredith2006}, based on the single large Southern Ocean wind event in 1999.
+ This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg2006}, in which a delayed amplification of the EKE response can occur through the topographic steering of currents away from the zonal direction, which decreases the stability of the current.
 

### 2022-01-06 paper/main.tex
updating paper to incorporate comments from Sally and Thierry

--- 2021-09-27 paper/main.tex
@@
 
-%%%%%%%
-% As of 2018 we recommend use of the TrackChanges package to mark revisions.
-% The trackchanges package adds five new LaTeX commands:
-%
-%  \note[editor]{The note}
-%  \annote[editor]{Text to annotate}{The note}
-%  \add[editor]{Text to add}
-%  \remove[editor]{Text to remove}
-%  \change[editor]{Text to remove}{Text to add}
-%
-% complete documentation is here: http://trackchanges.sourceforge.net/
-%%%%%%%
-
-%% Enter journal name below.
-%% Choose from this list of Journals:
-%
-% JGR: Atmospheres
-% JGR: Biogeosciences
-% JGR: Earth Surface
-% JGR: Oceans
-% JGR: Planets
-% JGR: Solid Earth
-% JGR: Space Physics
-% Global Biogeochemical Cycles
-% Geophysical Research Letters
-% Paleoceanography and Paleoclimatology
-% Radio Science
-% Reviews of Geophysics
-% Tectonics
-% Space Weather
-% Water Resources Research
-% Geochemistry, Geophysics, Geosystems
-% Journal of Advances in Modeling Earth Systems (JAMES)
-% Earth's Future
-% Earth and Space Science
-% Geohealth
-%
-% ie, \journalname{Water Resources Research}
-
 \journalname{JGR: Oceans}
@@
 \justify
-\title{Circumpolar variations in Southern Ocean eddy dynamics: insights from an ensemble modelling approach}
+\title{Circumpolar variations in the chaotic nature of Southern Ocean eddy dynamics}
 
@@
 \begin{keypoints}
-\item Variability in the Southern Ocean eddy field are dominated by intrinsic, rather than forced, processes.
+\item Variability in the Southern Ocean eddy field is dominated by chaotic, rather than forced, processes.
 \item The forced component of the eddy kinetic energy variance is significantly correlated with the local wind stress input.
@@
 The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
-The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic variability associated with the turbulent flow field itself.\footnote{{\color{red}Thierry: I agree, but some studies (e.g.
-Colin de Verdiere \& Huck 1999, Huck et al 2015) have mentioned that non-eddying ocean models can also produce (a small amount of) intrinsic variability via large-scale baroclinic instability.
-Need to mention?}}
+The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic, or chaotic, variability associated with the turbulent flow field itself.
 Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
-We find that intrinsic processes dominate the eddy field.
+We find that chaotic processes dominate the eddy field, even on longer timescales.
 Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
@@
 
-{\color{red}General Remarks by Thierry:
-
-\begin{itemize}
-	\item
-	Adopting the word intrinsic to name fluctuations around the ensemble mean is 100\% OK.
-But these fluctuations are also chaotic (in a broad sense), which implies that they limit predictability (as stated in the conclusion) and question the attribution of observed/simulated events to atmospheric drivers.
-In other words, the chaotic behavior of this variability is perhaps more important than its intrinsic origin, since it raises more concrete issues.
-This could maybe be stated more directly (?)
-
-	\item 
-	The fact that high-freq eddy variability is random/chaotic is well-known, and one of the main messages of the paper is that this character remains strong (and even dominant) over large regions and at long timescales (interannual).
-I suggest to insist a bit more on this (abstract, conclusion), which confirms our previous results on other variables (e.g.
-Leroux et al 2018, Serazin et al 2017, etc) : eddy chaos inversely cascades toward larger/longer scales and affects climate-relevant features (see Serazin et al 2018).
-
-\end{itemize}
-}
-
 %% ------------------------------------------------------------------------ %%
@@
 The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
-The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2021}.
+The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2022}.
 However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
@@
 Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
-Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship, and the role of intrinsic variability, need to be clarified.\footnote{{\color{red}Thierry: the notion of intrinsic variability could be introduced a bit more before this, explaining for instance that it emerges frrom oceanic non-linearities under constant or seasonal forcing and persists under variable forcing \citep{Leroux2018}, it has a random phase (``chaotic'' character), it mostly emerges at mesoscale and can cascade toward interannual to decadal time scales and O(1000$\,$km) space scales \cite{Serazin-etal-2018}.}}
+Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship needs to be clarified.
 
@@
 When fine graining these calculations it was found that only a single region (30$^\circ$ in longitude) expressed a significant long-term trend in EKE.
-This finding  suggests that previous characterisations of the response may have been dominated by a small number of regional events, and that at other times the intrinsic variance may dominate the signal.
+This finding  suggests that previous characterisations of the response may have been dominated by a small number of regional events, calling into question the robustness of previous studies.
 
-Thus, despite the proposed importance of the Southern Ocean eddy field to ocean circulation, the nature of the EKE variability remains unclear.
-A primary complication is what can be inferred from an admittedly short satellite record; in particular, whether individual events can be attributed to forcing changes, or to intrinsic variability, or a combination of the two.
+The dynamical importance of the Southern Ocean eddy field, and uncertainty over the robustness of its variability and trends, motivate a deeper investigation into the processes that control Southern Ocean eddies.
+A key issue here is the extent to which the eddy field purely responds to external (atmospheric) forcing, versus the role of chaotic and intrinsic variability in determining eddy energy.
+The fact that high-frequency eddy variability is random and chaotic is well-known, and even non-eddying ocean models can also produce (a small amount of) intrinsic variability via large-scale baroclinic instability \citep[e.g.][]{DeVerdiere1999}.
+At longer timescales intrinsic variability can emerge from oceanic non-linearities under constant or seasonal forcing and persists under variable forcing \citep{Leroux2018}.
+Such intrinsic variabilty has a random phase (that is, it is chaotic in character); it mostly emerges at mesoscale and can cascade toward interannual time scales and O(1000$\,$km) space scales \citep{Serazin-etal-2018}.
+One of the goals of this work is characterise the spatiotemporal extent of chaotic, intrinsic, variability in determining  Southern Ocean EKE.
+
+A primary complication in understanding Southern Ocean EKE is the limitation of inference from an admittedly short satellite record; in particular, whether individual events can be attributed to forcing changes, or to intrinsic variability, or a combination of the two.
 In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in an ensemble of eddy-permitting ocean simulations.
-We use the OCCIPUT ensemble of global ocean/sea-ice hindcast simulations \citep{Penduff-etal-2014, Leroux2018}, a 50-member ensemble of hindcast simulations\footnote{{\color{blue}Sally: The definition of OCCIPUT perhaps need to be moved up here from the paragraph below?}}.
+We use the OceaniC Chaos – ImPacts, strUcture, predicTability (OCCIPUT) ensemble of global ocean/sea-ice hindcast simulations \citep{Penduff-etal-2014, Leroux2018}, a 50-member ensemble of hindcast simulations.
 We examine both the intrinsic variance of the eddy field, and extract the ``forced'' (ensemble mean) component of the variability.
@@
 The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
-We use output from the OCCIPUT (OceaniC Chaos – ImPacts, strUcture, predicTability) ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} \footnote{{\color{blue}Sally: I think there's a problem in the bibtex file here: the citation seems to be coming up as Bernard instead of Barnier}}of the NEMO modelling system \citep{Madec2012}.
-The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels.
-We employ the probabilistic ocean modelling approach outlined by \citet{Bessieres2017}: \emph{(i)}~the 50 ensemble members are initialized in 1960 from a one-member 21-year spinup; \emph{(ii)}~the ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} during one year in 1960, which is shut off afterwards; \emph{(iii)}~the 50 ensemble members are driven between 1960 and 2015 by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}); the wind stress is computed without ocean current feedbacks, hence ensuring that the same momentum fluxes are applied to all members.
+We use output from the OCCIPUTensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}.
+The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels. We employ the probabilistic ocean modelling approach outlined by \citet{Bessieres2017}: 
+\begin{enumerate}
+\item The 50 ensemble members are initialized in 1960 from a single-member 21-year spinup;
+\item The ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} over one year (1960), after which the perturbation is terminated;
+\item The 50 ensemble members are driven between 1960 and 2015 by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}).
+\end{enumerate}
+In these simulations the wind stress is computed without ocean current feedbacks, hence ensuring that the same momentum fluxes are applied to all members. 
 We focus our analyses on the period 1980-2015, thus yielding an effective spinup duration of 41 years in each member.
@@
 \subsection{Estimating geostrophic eddy velocity}
-For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member) .
-{\color{blue} Sally: For each ensemble member, the member's global mean sea level anomaly is subtracted from all grid points at every time step to correct for spurious terms introduced by the use of the Boussinesq approximation \citep{Greatbatch1994}.
-The model drift, which is potentially nonlinear, is then corrected for by detrending using a LOWESS filter \citep{Cleveland1979} in combination with a 5th-order spline; full details of this preprocessing may be found in \citep{Close2020}.}
+For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member). 
+For each ensemble member, the member's global mean sea level anomaly is subtracted from all grid points at every time step to correct for spurious terms introduced by the use of the Boussinesq approximation \citep{Greatbatch1994}.
+The model drift, which is potentially nonlinear, is then corrected for by detrending using a LOWESS filter \citep{Cleveland1979} in combination with a 5th-order spline; full details of this preprocessing may be found in \cite{Close2020}.
 
@@
 \end{linenomath*}
-where $\overline{\cdot}$ represents the temporal average\footnote{{\color{blue}Sally: see above: instead of the temporal average it's the nonlinear trend that's removed}} over the simulation.
+where $\overline{\cdot}$ represents the temporally filtered sea level \citep{Close2020}.
 The sea level anomaly is detrended, and then used to calculate the eddy velocity field.
@@
 Anomalous values of $\mathbf{u}_i'$ close to coastlines are removed.
-
-\andycomment{Sally to add details about SLA processing?}
 
@@
 The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is encapsulated by this ensemble mean quantity.
-On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,\footnote{{\color{red}Thierry: instead of using the prime exponent (used for temporal anomalies), I suggest using e.g.
-a star (*) exponent for ensemble anomalies.}}
+On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
 \begin{linenomath*}
 \begin{equation}
-E_i' = E_i - \langle E_i \rangle.
+E_i^* = E_i - \langle E_i \rangle,
 \end{equation}
 \end{linenomath*}
+where $\cdot^*$ is used to indicate departure from the ensemble mean.
 With these expressions in hand, we follow \citet{Leroux2018} to define the  time-variance of the ensemble-mean EKE,
@@
 \begin{equation}
-\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i'(t)^2,
+\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i^*(t)^2,
 \end{equation}
@@
 The intensity of the Southern Ocean eddy field is not uniform.
-Snapshots of eddy kinetic energy (e.g.
-Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
-The same patterns are evident in the ensemble and temporal mean of the EKE (Fig.~\ref{Fig:1}b), although the signal of individual eddies is not longer apparent.
-The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is generally weak south of 60$^\circ$S.
-The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.
+Snapshots of eddy kinetic energy (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
+The same patterns are evident in the ensemble and temporal mean of the eddy energy ($\langle\textrm{EKE}\rangle$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
+The strongest band of $\langle\textrm{EKE}\rangle$ approximately follows the path of the Antarctic Circumpolar Current, and $\langle\textrm{EKE}\rangle$  is weak south of 60$^\circ$S.
+The patterns of $\langle\textrm{EKE}\rangle$  in this model broadly match the regional variations of $\langle\textrm{EKE}\rangle$  observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.
 
@@
 For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member in thin grey lines in Fig.~\ref{Fig:2}(a).
-This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of intrinsic variability in the Southern Ocean eddy field.
+This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
 Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
@@
 \caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S).
-(a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
+(a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation between wind stress and EKE for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
 \label{Fig:2}
@@
 The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
-On the other hand, ensemble member 5 (magenta line) has a clear (and significant; $T = 5.5$) correlation with a 4-month lag, while member 25 (orange line) is correlated weakly at 6 months, and significantly correlated ($T = 4.2$) at a 24-month lag.
+On the other hand, ensemble member 5 (magenta line) has a clear (and significant; $T = 5.5$) correlation with a 4-month lag, while member 25 (orange line) is weakly correlated at 6 months, and significantly correlated ($T = 4.2$) at a 24-month lag.
 These isolated examples highlight the differing behaviour of each ensemble member. 
 The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
-Thus, there appear to be two distinct timescales of response of the Southern Ocean eddy field to wind stress.
+Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model.
 
@@
 Calculating the variability of EKE in a smaller region has the advantage of isolating the individual processes which may occur in differing regions (for example, stronger topographic steering in places with steep bathymetry).
-However, this advantage is partly offset by higher intrinsic variability;  in cases where the region of interest is sufficiently small that an individual eddy or event can have a large influence over the EKE timeseries.
-In balancing these competing issues, we look at the variability within regions that span 15-20$^\circ$ in latitude and 30-40$^\circ$ in longitude, as shown in Figure \ref{Fig:3}(a).
+However, this advantage is partly offset by higher intrinsic variability;  if the region of interest is sufficiently small, then an individual eddy or event can have a large influence over the EKE timeseries.
+In balancing these competing issues, we examine the variability within regions that span 15-20$^\circ$ in latitude and 30-40$^\circ$ in longitude, as shown in Figure \ref{Fig:3}(a).
 We analyse the EKE timeseries averaged over these boxes -- including individual member EKE, ensemble mean EKE and lagged correlations between local wind stress forcing and the ensemble mean EKE in Fig.
@@
 We first examine a region in the lee of Kerguelen Plateau in the Southeast Indian Ocean (cyan box in Fig.~\ref{Fig:3}a).
-This region is characterised by high-frequency ($\sim$1 year) variations in EKE, with a relatively large forced component (the intrinsic variance fraction $R_i = 0.63$ which is smaller than the Southern Ocean average; Fig.~\ref{Fig:3}b).
+This region is characterised by high-frequency ($\sim$1 year) variations in EKE, with a relatively large forced component (the intrinsic variance fraction, $R_i = 0.63$, is smaller than the Southern Ocean average; Fig.~\ref{Fig:3}b).
 The forced variation is clearly evident in the timeseries of  individual ensemble members; and this forced component is related to wind stress.
-The lag between wind stress variations and ensemble mean EKE is short ($\sim$ 5 months; Fig.~\ref{Fig:3}c) with a single clear  and significant peak in the lagged correlation.
+The lag between wind stress variations and ensemble mean EKE is short ($\sim$ 5 months; cyan line in Fig.~\ref{Fig:3}c) with a single clear  and significant peak in the lagged correlation.
 There is a second, weaker but significant, correlation at 30 months lag.
@@
 Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
-The maximum values in the lag correlation occurs over a broad band from 9-24 months in this region, without a single clear peak.
+The maximum values in the lag correlation occur over a broad band from 9-24 months in this region, without a single clear peak.
 Thus, this region varies slowly and consistently to interannual variations in wind stress.
@@
 Other regions (see Fig.
-\ref{Fig:4}) highlight different aspects of the response;  with almost no correlation with wind forcing over the Central South Pacific ( Fig.
+\ref{Fig:4}) highlight different aspects of the local eddy response;  with almost no correlation with wind forcing over the Central South Pacific ( Fig.
 \ref{Fig:4}b) or the Southwest Indian Ocean  (the Agulhas meander region; Fig.
@@
 \includegraphics[width=\hsize]{Figure5}
-\caption{The spatial correlation of wind stress with EKE in (a) the Southeast Indian Ocean at 5-month lag; (b) the Southeast Indian Ocean at 30-month lag; (c) the Southwest Pacific ocean at 15-month lag and (d) the South Atlantic Ocean at 17-month lag.}
+\caption{The spatial correlation of wind stress with $\langle\textrm{EKE}\rangle$ in (a) the Southeast Indian Ocean at 5-month lag; (b) the Southeast Indian Ocean at 30-month lag; (c) the Southwest Pacific ocean at 15-month lag and (d) the South Atlantic Ocean at 17-month lag.}
 \label{Fig:5}
@@
 In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
-These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle\textrm{EKE}\rangle$ occurs within the $\langle\textrm{EKE}\rangle$)-averaging region.
-This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the $\langle\textrm{EKE}\rangle$-averaging region is not stronger than within the $\langle\textrm{EKE}\rangle$)-averaging region.
-A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
+These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle\textrm{EKE}\rangle$ occurs within the $\langle\textrm{EKE}\rangle$-averaging region.
+This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the $\langle\textrm{EKE}\rangle$-averaging region is not stronger than within the $\langle\textrm{EKE}\rangle$-averaging region.
+A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing to the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
 Importantly, there is no suggestion of a strong correlation with wind stress upstream of the $\langle\textrm{EKE}\rangle$-averaging region.
@@
 Thus, these spatial maps demonstrate that, where strong forced variability in the $\langle\textrm{EKE}\rangle$ exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
-
-{\color{red}Navid: Thierry, did I make all the appropriate changes EKE $\to$ $\langle\textrm{EKE}\rangle$ correctly?}
 
@@
 This point is clarified in Fig.~\ref{Fig:6} which shows a map of the intrinsic fraction of variance, $R_i$, from eddy statistics interpolated onto a coarse 5$^\circ \times$5$^\circ$ grid.
-Here, the intrinsic variance is close to unity over most of the band of elevated EKE in the Southern Ocean. 
-Subpanels (b) and (c) confirm the predominance of intrinsic eddy variability at this scale, highlighting that at small scales we can place little reliability on the results from an individual ensemble member.
+Here, the chaotic variance dominates over most of the band of elevated EKE in the Southern Ocean. 
+Subpanels (b) and (c) confirm the predominance of intrinsic eddy variability at this scale, highlighting that at small scales we can place little reliability on the results from an individual ensemble member, or a single observation.
 
@@
 Both of these regions are locations where topography acts to sharpen and energise fronts.
-However, in many other regions, EKE variability appears to be almost entirely due to intrinsic processes.
+However, in many other regions, EKE variability appears to be almost entirely chaotic.
 This heterogeneity, consistent with the findings of \citet{Patara2016}, acts to emphasise the differing flow regimes which are found in different parts of the Southern Ocean.
 
-Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and EKE: one at 4 months, and the other at $\sim$30 months.
+Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and $\langle\textrm{EKE}\rangle$: one at 4 months, and the other at $\sim$30 months.
 The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
@@
 
-The ensemble approach thus leads to the conclusion that eddy processes in the Southern Ocean include a large component of intrinsic variability, even when averaged over a large spatial area and up to interannual time scales.
+The ensemble approach thus leads to the conclusion that eddy processes in the Southern Ocean include a large component of chaotic variability, even when averaged over a large spatial area and up to interannual time scales.
 This result argues for caution in interpreting observations of Southern Ocean eddies, which are necessarily based on a single, short realisation of the natural world.
@@
 PIRATE has been funded by CNES through the Ocean Surface Topography Science Team (OST-ST). 
-{\color{red}The model output used in this study can be downloaded from the Zenodo repository at doi:XXX.XXX.XXX.
-The full OCCIPUT model dataset is available on request (\href{mailto:Thierry.Penduff@cnrs.fr}{Thierry.Penduff@cnrs.fr}).}
+{\color{red}The model output used in this study can be downloaded from the Zenodo repository at doi:XXX.XXX.XXX.}
+The full OCCIPUT model dataset is available on request (\href{mailto:Thierry.Penduff@cnrs.fr}{Thierry.Penduff@cnrs.fr}).
 

### 2022-01-06 paper/main.tex
fixing line numbers
final minor edits to second draft

@@
 
-\documentclass{agujournal2019}
+\documentclass[linenumbers]{agujournal2019}
 
 \graphicspath{ {figures/} }
-\usepackage{lineno,layouts,microtype}
+%\usepackage{lineno,layouts,microtype}
 
@@
 
-\linenumbers
+%\linenumbers
 
@@
 \usepackage{amsfonts, amssymb, amsmath}
-\usepackage[labelfont=bf]{caption}
+%\usepackage[labelfont=bf]{caption}
 
@@
 \authors{
-Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez Moreno\affil{1}
+Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez-Moreno\affil{1}
 }
@@
 \item The forced component of the eddy kinetic energy variance is significantly correlated with the local wind stress input.
-\item The eddy field lags the wind stress, with two clear timescales emerging: one at $\sim$6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
+\item The eddy field lags the wind stress, with two clear timescales emerging: one at 4-6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
 \end{keypoints}
@@
 The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic, or chaotic, variability associated with the turbulent flow field itself.
-Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forcing and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
-We find that chaotic processes dominate the eddy field, even on longer timescales.
-Where correlations between the forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
+Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forced and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
+We find that chaotic processes dominate the eddy field, even on longer (interannual) timescales.
+Where correlations between the wind stress forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
 These results suggest that understanding Southern Ocean eddy dynamics and its larger-scale impacts requires an ensemble approach to eliminate intrinsic variability, and therefore may not yield robust conclusions from observations alone.
@@
 \noindent The Southern Ocean is the most turbulent part of the world's oceans.
-The variations in this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
+The variation of this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
 But it's hard to get information about these eddies, because they occur on small scales in a large ocean basin that is poorly observed.
@@
 The chaotic nature of the turbulent ocean means that these model runs exhibit different evolutions.
-We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external forcing that is common to all experiments (such as wind forcing).
+We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external factors that are common to all experiments (such as wind stress).
 We conclude that the Southern Ocean eddy field is dominated by intrinsic chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence.
@@
 The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2022}.
-However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that understanding the dynamics (with the aim of predicting future responses to climate change) need to be urgently constrained.
+However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that the dynamics of this region (with the aim of predicting future responses to climate change) need to be urgently constrained.
 
 Another unique feature of the Southern Ocean is that it has a strong eddy field \citep{Fu2010}.
-This strong eddy field has been suggested to be important in the Southern Ocean's response to change.
+This eddy field has been suggested to be important in the Southern Ocean's response to change.
 For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
@@
 \citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
-\citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship is variable around the Southern Ocean.
+\citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship varies in strength around the Southern Ocean.
 Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
@@
 The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by \citet{Zhang2021}, who used crossover data from satellite observations \citep[as in][]{Hogg2015} to better estimate the EKE on regional scales.
-When fine graining these calculations it was found that only a single region (30$^\circ$ in longitude) expressed a significant long-term trend in EKE.
+When fine-graining these calculations it was found that only a single region (30$^\circ$ in longitude) expressed a significant long-term trend in EKE.
 This finding  suggests that previous characterisations of the response may have been dominated by a small number of regional events, calling into question the robustness of previous studies.
@@
 A key issue here is the extent to which the eddy field purely responds to external (atmospheric) forcing, versus the role of chaotic and intrinsic variability in determining eddy energy.
-The fact that high-frequency eddy variability is random and chaotic is well-known, and even non-eddying ocean models can also produce (a small amount of) intrinsic variability via large-scale baroclinic instability \citep[e.g.][]{DeVerdiere1999}.
+The fact that high-frequency eddy variability is random and chaotic is well-known, and even non-eddying ocean models can produce (a small amount of) intrinsic variability via large-scale baroclinic instability \citep[e.g.][]{DeVerdiere1999}.
 At longer timescales intrinsic variability can emerge from oceanic non-linearities under constant or seasonal forcing and persists under variable forcing \citep{Leroux2018}.
@@
 The methodology employed in this study is derived from the probabilistic approach to ocean modelling outlined by \citet{Bessieres2017}.
-We use output from the OCCIPUTensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}.
-The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels. We employ the probabilistic ocean modelling approach outlined by \citet{Bessieres2017}: 
+We use output from the OCCIPUT ensemble of 50 eddy-permitting global ocean--sea ice simulations, based on the ORCA025 implementation \citep[e.g.][]{Barnier2006} of the NEMO modelling system \citep{Madec2012}.
+The model grid has a 1/4$^\circ$ horizontal resolution and 75 geopotential levels. 
+The approach involves:
 \begin{enumerate}
@@
 \item The ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} over one year (1960), after which the perturbation is terminated;
-\item The 50 ensemble members are driven between 1960 and 2015 by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}).
+\item The 50 ensemble members are integrated from 1960 to 2015, driven by the same realistic atmospheric forcing function based on the ERA-40 and ERA-Interim reanalyses (Drakkar Forcing Set DFS5.2; \citet{Dussin-etal-2016}).
 \end{enumerate}
@@
 \end{linenomath*}
-where $\overline{\cdot}$ represents the temporally filtered sea level \citep{Close2020}.
-The sea level anomaly is detrended, and then used to calculate the eddy velocity field.
+where $\overline{\cdot}$ represents the temporally filtered, detrended sea level \citep{Close2020}.
+The sea level anomaly is then used to calculate the eddy velocity field.
 Surface eddy velocity in each ensemble member, $\mathbf{u}_i' = (u_i', v_i')$ is estimated from the detrended sea level anomaly via the geostrophic relation,
@@
 \end{linenomath*}
-When $R_i$ approaches unity, the system is dominated by intrinsic variability, and at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.
+When $R_i$ approaches unity, the system is dominated by intrinsic variability, while at the limit  of $R_i \to 0$ the system is solely responding to forced variability induced by atmospheric forcing.
 
@@
 The intensity of the Southern Ocean eddy field is not uniform.
-Snapshots of eddy kinetic energy (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
-The same patterns are evident in the ensemble and temporal mean of the eddy energy ($\langle\textrm{EKE}\rangle$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
-The strongest band of $\langle\textrm{EKE}\rangle$ approximately follows the path of the Antarctic Circumpolar Current, and $\langle\textrm{EKE}\rangle$  is weak south of 60$^\circ$S.
-The patterns of $\langle\textrm{EKE}\rangle$  in this model broadly match the regional variations of $\langle\textrm{EKE}\rangle$  observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.
+A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
+The same patterns are evident in the ensemble and temporal mean of the EKE ($\overline{\langle E_i \rangle}$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
+The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is weak south of 60$^\circ$S.
+The patterns of EKE in this model broadly match the regional variations of EKE observed from satellite altimetry, albeit at slightly lower intensity, as expected in an eddy-permitting model \citep[e.g.][]{Kiss2020}.
 
@@
 Although Southern Ocean EKE variability is strongly intrinsic, there remains a component of forced variability (red line in Fig.~\ref{Fig:2}a).
-Previous studies have suggested that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
+Previous studies have inferred that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
 This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results.
-However, the time-lagged correlations between wind stress and EKE suggests that this relationship is complex. 
+However, the time-lagged correlations between wind stress and EKE implies that this relationship is complex. 
 The intrinsically variable nature of Southern Ocean eddies means that for some ensemble members, there is no meaningful correlation between wind stress and eddies (grey lines in Fig~\ref{Fig:2}b).
@@
 \caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
-(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (c) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+(a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
 The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
@@
 
-In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation is clearly different.
+In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation clearly differs.
 Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
@@
 \caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
-(a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+(a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
 The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
@@
 \includegraphics[width=\hsize]{Figure5}
-\caption{The spatial correlation of wind stress with $\langle\textrm{EKE}\rangle$ in (a) the Southeast Indian Ocean at 5-month lag; (b) the Southeast Indian Ocean at 30-month lag; (c) the Southwest Pacific ocean at 15-month lag and (d) the South Atlantic Ocean at 17-month lag.}
+\caption{The spatial correlation of wind stress with $\langle E_i \rangle$ in (a) the Southeast Indian Ocean at 5-month lag; (b) the Southeast Indian Ocean at 30-month lag; (c) the Southwest Pacific ocean at 15-month lag and (d) the South Atlantic Ocean at 17-month lag.}
 \label{Fig:5}
@@
 
-The heterogeneity in correlations between local wind and the ensemble-mean EKE ($\langle\textrm{EKE}\rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
+The heterogeneity in correlations between local wind and the ensemble mean EKE ($\langle E_i \rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
 However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
@@
 To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}).
-To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with ensemble-mean EKE at different lags.
+To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with ensemble mean EKE at different lags.
 In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
-These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle\textrm{EKE}\rangle$ occurs within the $\langle\textrm{EKE}\rangle$-averaging region.
-This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the $\langle\textrm{EKE}\rangle$-averaging region is not stronger than within the $\langle\textrm{EKE}\rangle$-averaging region.
+These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle E_i \rangle$ occurs within the EKE-averaging region.
+This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
 A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing to the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
-Importantly, there is no suggestion of a strong correlation with wind stress upstream of the $\langle\textrm{EKE}\rangle$-averaging region.
-In the South Atlantic, the $\langle\textrm{EKE}\rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
-Thus, these spatial maps demonstrate that, where strong forced variability in the $\langle\textrm{EKE}\rangle$ exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
+Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKEaveraging region.
+In the South Atlantic, the $\langle E_i \rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
+Thus, these spatial maps demonstrate that, where strong forced variability in the ensemble mean EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
 
@@
 The simulations shown here advocate for a probabilistic approach to understanding the Southern Ocean eddy field.
-The 50-member ensemble of eddy-permitting ocean-sea ice model simulations investigated here demonstrate that inference about the EKE response of a single ensemble member to variable forcing in a localised region is not robust, consistent with the inference of \citet{Zhang2021}.
-This point is clarified in Fig.~\ref{Fig:6} which shows a map of the intrinsic fraction of variance, $R_i$, from eddy statistics interpolated onto a coarse 5$^\circ \times$5$^\circ$ grid.
-Here, the chaotic variance dominates over most of the band of elevated EKE in the Southern Ocean. 
+The 50-member ensemble of eddy-permitting ocean-sea ice model simulations investigated here demonstrate that inference about the EKE response of a single ensemble member to variable forcing in a localised region is not robust, broadly consistent with the findings of \citet{Zhang2021}.
+This point is clarified in Fig.~\ref{Fig:6} which shows a map of the intrinsic fraction of interannual variance, $R_i$, from eddy statistics interpolated onto a coarse (4$^\circ \times$4$^\circ$) grid, with eddy contributions filtered using a 12-month rolling mean.
+Here, even at interannual timescales, the chaotic variance dominates over most of the band of elevated EKE in the Southern Ocean. 
 Subpanels (b) and (c) confirm the predominance of intrinsic eddy variability at this scale, highlighting that at small scales we can place little reliability on the results from an individual ensemble member, or a single observation.
@@
 \begin{center}
-\includegraphics[width=\hsize]{Figure6}
-\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  5$^\circ \times$5$^\circ$ grid; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes.
-{\color{red}(Thierry: How about adding to this figure the same 3 maps for the interannual EKE variability alone?
-This would explicitly show that intrinsic signals remain strong even at low-frequencies: this can be explicitly stated in the text.)}}
+\includegraphics[width=\hsize]{Figure7}
+\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  4$^\circ \times$4$^\circ$ grid and with a 12-month rolling mean; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes.
+}
 \label{Fig:6}
@@
 
-Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and $\langle\textrm{EKE}\rangle$: one at 4 months, and the other at $\sim$30 months.
+Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and the ensemble mean EKE: one at 4-6 months, and the other at $\sim$30 months.
 The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
@@
 Given that eddies are critical for the Southern Ocean circulation, this result implies that predictability of the future Southern Ocean may be weaker than previously thought.
-It also highlights the difficulty faced in distinguishing the processes that govern eddy dynamics in this system, and point to more systematic eddy identification and modelling studies to better isolate these processes.
+The results outlined here also highlight the difficulty faced in distinguishing the processes that govern eddy dynamics in this system, and point to more systematic eddy identification and modelling studies to better isolate these processes.
 

### 2022-01-06 paper/main.tex
altering description of delayed timescale

@@
 The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
-The slower timescale is similar to that proposed by \citet{Meredith-Hogg-2006}, based on the single large Southern Ocean wind event in 1999.
-This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg-Blundell-2006}, in which a delayed amplification of the EKE response can occur through the topographic steering of currents away from the zonal direction, which decreases the stability of the current.
+This mechanism the direct eddy response to wind stress changes via baroclinic instability.
+
+The slower timescale is similar to that proposed by \citet{Meredith-Hogg-2006}, based on a single large Southern Ocean wind event in 1999.
+This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg-Blundell-2006}.
+Under this mechanism, the system first responds directly, via baroclinic instability, as described above. 
+The stronger eddy field acts to increase the vertical momentum transfer which enables topography to steer the current and thereby increase the meridional component of the mean flow. 
+Currents with a non-zonal component are more susceptible to baroclinic instability which thus produces a delayed amplification of the EKE response.
+This mechanism describes a positive feedback between the eddy field and the mean currents which acts to enhance EKE over longer timescales.
 

### 2022-01-07 paper/main.tex
minor changes to the paper in response to navids suggestions

@@
 \noindent The Southern Ocean is the most turbulent part of the world's oceans.
-The variation of this turbulence, which is often referred to as \emph{eddies}, is critical to understanding the evolution of the Southern Ocean under climate change.
+This turbulence, often referred to as \emph{eddies}, is critical to the evolution of the Southern Ocean under climate change.
 But it's hard to get information about these eddies, because they occur on small scales in a large ocean basin that is poorly observed.
-In addition, the observational record is quite short, which makes it more difficult to use these observations to study what controls variation in the eddy field.
+In addition, the observational record is quite short, which makes it more difficult to use these observations to study what controls variations of these eddies.
 For this reason, we take an eddy-permitting ocean model, and run it 50 times with the same forcing (but a slightly different initial state).
 The chaotic nature of the turbulent ocean means that these model runs exhibit different evolutions.
-We thus use these simulations to study which eddy processes are intrinsic (that is, a consequence of the chaotic nature of turbulence) and which are forced by the external factors that are common to all experiments (such as wind stress).
-We conclude that the Southern Ocean eddy field is dominated by intrinsic chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence.
+Then we use these simulations to study which eddy processes occur as a consequence of the chaotic nature of turbulence and which are forced by the external factors that are common to all model runs (such as wind stress).
+We conclude that the Southern Ocean eddy field is dominated by chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence.
 \end{abstract}
@@
 
-The Southern Ocean is unique in the global ocean; it is the one region without continents on its zonal boundaries, giving rise to the Antarctic Circumpolar Current (ACC) which flows eastward around the globe.
+The Southern Ocean is unique in the global ocean; it is the one region without continents on its zonal boundaries, giving rise to the Antarctic Circumpolar Current (ACC) that flows eastward around the globe.
 The ACC acts to connect the other major basins and thereby regulates climate and nutrients.
@@
 Eddy kinetic energy has a complex relationship with the forces that drive the ocean circulation.
-\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between events in wind stress forcing and EKE anomalies.
+\citet{Meredith-Hogg-2006} found significant variations in the area-averaged eddy field in some regions, and argued for a 2-3 year lag between wind stress forcing variations and EKE anomalies that follow.
 \citet{Patara2016}, using a realistic high-resolution ocean model found that EKE does have a lagged response to wind stress anomalies, but that this relationship varies in strength around the Southern Ocean.
-Idealised models over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
+Idealised model studies over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
 Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship needs to be clarified.
 
-On longer timescales it has also been proposed that EKE has increased over recent decades \citep{Hogg2015, Martinez-Moreno2019, Martinez-Moreno2021-ncc}.
+On longer timescales, it has also been proposed that EKE has increased over recent decades \citep{Hogg2015, Martinez-Moreno2019, Martinez-Moreno2021-ncc}.
 The robustness of this wind-EKE relationship in the Southern Ocean was recently investigated by \citet{Zhang2021}, who used crossover data from satellite observations \citep[as in][]{Hogg2015} to better estimate the EKE on regional scales.
-When fine-graining these calculations it was found that only a single region (30$^\circ$ in longitude) expressed a significant long-term trend in EKE.
+By fine-graining these calculations it was found that only a single region (30$^\circ$-wide in longitude) expressed a significant long-term trend in EKE.
 This finding  suggests that previous characterisations of the response may have been dominated by a small number of regional events, calling into question the robustness of previous studies.
@@
 A key issue here is the extent to which the eddy field purely responds to external (atmospheric) forcing, versus the role of chaotic and intrinsic variability in determining eddy energy.
-The fact that high-frequency eddy variability is random and chaotic is well-known, and even non-eddying ocean models can produce (a small amount of) intrinsic variability via large-scale baroclinic instability \citep[e.g.][]{DeVerdiere1999}.
+The fact that high-frequency eddy variability is random and chaotic is well-known, and even non-eddying ocean models can produce (a small amount of) intrinsic variability via large-scale baroclinic instability \citep[e.g.][]{DeVerdiere1999,Constantinou2021}.
 At longer timescales intrinsic variability can emerge from oceanic non-linearities under constant or seasonal forcing and persists under variable forcing \citep{Leroux2018}.
@@
 and subsampled at monthly temporal resolution.
-It is notable that $E_i$ contains a large component of seasonal variation \citep{Martinez-Moreno2021} which dominates the statistics.
+It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2021}.
 To look at the forced response, we therefore deseasonalise $E_i$, by removing the climatological mean for each month.

### 2022-01-09 paper/main.tex
Updating for Sally, Bill, Josue final comments

@@
 \authors{
-Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez-Moreno\affil{1}
+Andrew McC. Hogg\affil{1}, Thierry Penduff\affil{2}, Sally E. Close\affil{2,4}, William K. Dewar\affil{3},\\Navid C. Constantinou\affil{1}, \quad and\quad Josu{\'e} Mart{\'i}nez-Moreno\affil{1,4}
 }
@@
 \affiliation{3}{Florida State University, Tallahassee, FL, USA}
+\affiliation{4}{Now at: Laboratoire d'Oc\'eanographie Physique et Spatiale (LOPS), University of Brest/IFREMER/IRD/CNRS, Brest, France}
 
@@
 A similar result is found in the Southwest Pacific Ocean (Fig.~\ref{Fig:5}c); wind stress correlations are relatively uniform across the Pacific Ocean owing to the autocorrelation of winds, but the correlations are less circumpolar than the Southeast Indian Ocean.
-Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKEaveraging region.
+Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKE-averaging region.
 In the South Atlantic, the $\langle E_i \rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
@@
 The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
-This mechanism the direct eddy response to wind stress changes via baroclinic instability.
+This mechanism is the direct eddy response to wind stress changes via baroclinic instability.
 
@@
 PIRATE has been funded by CNES through the Ocean Surface Topography Science Team (OST-ST). 
+WKD was funded by ANR-18-MPGA-0002 and NSF grants oce-182956 and oce-2023585.
 {\color{red}The model output used in this study can be downloaded from the Zenodo repository at doi:XXX.XXX.XXX.}

### 2022-01-13 paper/main.tex
final updates from Thierry -- Submitted Version

@@
 \begin{keypoints}
-\item Variability in the Southern Ocean eddy field is dominated by chaotic, rather than forced, processes.
+\item Monthly-to-interannual variability in the Southern Ocean eddy field is dominated by chaotic, rather than atmospherically-forced processes.
 \item The forced component of the eddy kinetic energy variance is significantly correlated with the local wind stress input.
-\item The eddy field lags the wind stress, with two clear timescales emerging: one at 4-6 months, which we attribute to baroclinic instability, and one at 2-3 years, which we attribute to the delayed effect of topographic steering.
+\item The forced changes in the eddy field lag the wind stress, with two timescales emerging: one at 4-6 months, and one at 2-3 years.
 \end{keypoints}
@@
 The effect of Southern Ocean eddies on the ocean circulation is significant -- they modulate the momentum balance of the zonal flow, and the meridional transport of tracers and mass.
-The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic, or chaotic, variability associated with the turbulent flow field itself.
+The strength of the eddy field is controlled by a combination of forcing (primarily thought to be wind stress) and intrinsic, chaotic, variability associated with the turbulent flow field itself.
 Here, we present results from an eddy-permitting ensemble of ocean model simulations to investigate the relative contribution of forced and intrinsic processes in governing the variability of Southern Ocean eddy kinetic energy.
-We find that chaotic processes dominate the eddy field, even on longer (interannual) timescales.
+We find that variations of the eddy field are mostly random, even on longer (interannual) timescales.
 Where correlations between the wind stress forcing and the eddy field exist, these interactions are dominated by two distinct timescales -- a fast baroclinic instability response; and a multi-year process owing to feedback between bathymetry and the mean flow.
@@
 Then we use these simulations to study which eddy processes occur as a consequence of the chaotic nature of turbulence and which are forced by the external factors that are common to all model runs (such as wind stress).
-We conclude that the Southern Ocean eddy field is dominated by chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence.
+We conclude that monthly-to-interannual fluctuations of the Southern Ocean eddy field are dominated by chaotic processes; but that the forced variability responds to wind on particular timescales that are controlled by the mechanisms that generate ocean turbulence.
 \end{abstract}
@@
 A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
-Therefore, the response of fine scale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.
+Therefore, the response of mesoscale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.
 
@@
 Such intrinsic variabilty has a random phase (that is, it is chaotic in character); it mostly emerges at mesoscale and can cascade toward interannual time scales and O(1000$\,$km) space scales \citep{Serazin-etal-2018}.
-One of the goals of this work is characterise the spatiotemporal extent of chaotic, intrinsic, variability in determining  Southern Ocean EKE.
+One of the goals of this work is to characterise the spatiotemporal extent of chaotic, intrinsic, variability in determining  Southern Ocean EKE.
 
 A primary complication in understanding Southern Ocean EKE is the limitation of inference from an admittedly short satellite record; in particular, whether individual events can be attributed to forcing changes, or to intrinsic variability, or a combination of the two.
-In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in an ensemble of eddy-permitting ocean simulations.
+In this paper, we address this question by examining the intrinsic variability of the Southern Ocean eddy field in a large ensemble of eddy-permitting ocean simulations.
 We use the OceaniC Chaos – ImPacts, strUcture, predicTability (OCCIPUT) ensemble of global ocean/sea-ice hindcast simulations \citep{Penduff-etal-2014, Leroux2018}, a 50-member ensemble of hindcast simulations.
@@
 
-The sea level anomaly, $\eta_i'$, is calculated as the transient component of sea level, given by 
+The sea level anomaly, $\eta_i'$, is calculated as the transient component of sea level in ensemble member $i$, given by 
 \begin{linenomath*}
@@
 It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2021}.
-To look at the forced response, we therefore deseasonalise $E_i$, by removing the climatological mean for each month.
+To look at the forced response, we therefore deseasonalise $E_i$, by removing mean seasonal cycle.
 We then proceed to compute ensemble statistics from this deseasonalised EKE.
@@
 \begin{equation}
-\langle E_i \rangle = \frac{1}{N} \sum_{i=1}^N E_i.
+\langle E \rangle = \frac{1}{N} \sum_{i=1}^N E_i.
 \end{equation}
 \end{linenomath*}
-The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is encapsulated by this ensemble mean quantity.
+The argument can be made that, since each ensemble member is forced with identical atmospheric conditions, the forced EKE response is captured by this ensemble mean quantity.
 On the other hand, the intrinsic variability of EKE in each ensemble member is found by taking the difference from the ensemble mean for each member,
@@
 \begin{equation}
-E_i^* = E_i - \langle E_i \rangle,
+E_i^* = E_i - \langle E \rangle,
 \end{equation}
@@
 \begin{equation}
-\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E_i \rangle -  \overline{\langle E_i \rangle}\right)^2,
+\sigma^2_{\langle E \rangle} = \frac{1}{T} \sum_{t=1}^T \left(\langle E \rangle -  \overline{\langle E \rangle}\right)^2,
 \end{equation}
@@
 To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
-Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $\tau$ (which is identical for all ensemble members) and EKE.
+Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $|\tau|$ (which is identical for all ensemble members) and EKE.
 For each correlation we evaluate the statistical significance of the correlation \citep[following, e.g.][]{Santer2000}.
@@
 The intensity of the Southern Ocean eddy field is not uniform.
-A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which occur in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
-The same patterns are evident in the ensemble and temporal mean of the EKE ($\overline{\langle E_i \rangle}$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
+A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which appear in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
+The same patterns are evident in the ensemble and temporal mean of the EKE ($\overline{\langle E \rangle}$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
 The strongest band of EKE approximately follows the path of the Antarctic Circumpolar Current, and EKE is weak south of 60$^\circ$S.
@@
 \includegraphics[width=\hsize]{Figure1}
-\caption{(a) Snapshot (5-day average) from a single ensemble member showing Southern Ocean EKE, $E_i$, and (b) time-averaged ensemble mean EKE, $\overline{\langle E_i\rangle}$.}
+\caption{(a) Snapshot (5-day average) from a single ensemble member showing Southern Ocean EKE, $E_i$, and (b) time-averaged ensemble mean EKE, $\overline{\langle E \rangle}$.}
 \label{Fig:1}
@@
 Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
-Averaged over this region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate eddy variability in the Southern Ocean eddy field.
+Averaged over this wide region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate the variability in the eddy field averaged over the basin.
 
@@
 The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
-Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model.
+Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model, overprinted by a dominanent and complex influence of chaotic variability.
 
@@
 The maximum values in the lag correlation occur over a broad band from 9-24 months in this region, without a single clear peak.
-Thus, this region varies slowly and consistently to interannual variations in wind stress.
+Thus, this region varies slowly and consistently to interannual variations in wind stress, albeit with a strong chaotic component.
 
-In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is again dominated by intrinsic variance ($R_i=0.74$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar variability of the EKE response to wind.
+In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is again dominated by intrinsic variance ($R_i=0.74$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar heterogeneity of the EKE response to wind.
 Other regions (see Fig.
@@
 \ref{Fig:4}e).
-In both of these regions, intrinsic variability dominates the signal and correlations are weak and insignificant. 
+In both of these regions, intrinsic variability largely dominates the signal and correlations are weak and insignificant. 
 On the other hand, the Southeast Pacific (north of the main pathway of the ACC) shows a strong and coherent multi-year response to wind stress, with smaller intrinsic variance fraction and a peak lag at 30 months.
 It is notable that this region, which is north of the mean ACC pathway, has a weak EKE signal (one tenth the magnitude of the core of the ACC).
-The circumpolar variation in both EKE response times and intrinsic variability suggests that the two-timescale response seen in Fig.
+The circumpolar contrasts in both EKE response times and intrinsic variability suggests that the two-timescale response seen in Fig.
 \ref{Fig:2} may be created by different processes, which each dominate in different regions of the Southern Ocean.
@@
 
-The heterogeneity in correlations between local wind and the ensemble mean EKE ($\langle E_i \rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
+The heterogeneity in correlations between local wind and the ensemble mean EKE ($\langle E \rangle$) shows that, where forced variability in Southern Ocean EKE occurs, it can be partly explained by variations in wind stress.
 However, these correlations are based purely on local wind stress -- averaged over the same area as the EKE statistics.
 The existence of multi-year lags between the wind and the EKE suggests that local winds may not be the only source of energy for eddy generation; in particular, it is possible that energy could be advected a considerable distance downstream during this lag period.
-To investigate this question we now take each of the regions outlined in Fig. \ref{Fig:3} and look at the spatial correlation between wind stress and the local ensemble mean EKE (Fig. \ref{Fig:5}).
+To investigate this question we now take each of the regions outlined in Fig.
+\ref{Fig:3} and look at the spatial distribution of temporal correlations between wind stress and the local ensemble mean EKE (Fig.
+\ref{Fig:5}).
 To make this calculation, wind stress is first coarsened to a 4$^\circ \times $4$^\circ$ grid, and wind stress in each of those coarsened grid cells correlated with ensemble mean EKE at different lags.
 In the Southeast Indian Ocean, Fig.~\ref{Fig:3}(c) shows correlation maxima at 5 months and 30 months; the spatial variation of this correlation is shown in Fig. \ref{Fig:5}(a,b) respectively.
-These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle E_i \rangle$ occurs within the EKE-averaging region.
+These figures highlight a key feature of Southern Ocean wind stress, which is that there are strong autocorrelations between wind stress along a line of latitude; nonetheless, the maximum correlation between wind stress and $\langle E \rangle$ occurs within the EKE-averaging region.
 This correlation is lower in magnitude at 30 months (consistent with Fig.~\ref{Fig:3}c), but at both 5 and 30 month lags the correlation with wind upstream of the EKE-averaging region is not stronger than within the EKE-averaging region.
@@
 Importantly, there is no suggestion of a strong correlation with wind stress upstream of the EKE-averaging region.
-In the South Atlantic, the $\langle E_i \rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
+In the South Atlantic, $\langle E \rangle$ is not strongly correlated with wind stress, either in the local region or elsewhere in the Southern Ocean (Fig.~\ref{Fig:5}d).
 Thus, these spatial maps demonstrate that, where strong forced variability in the ensemble mean EKE exists, it is most strongly linked to local wind stress, with no suggestion of upstream or remote wind input playing a strong role.
@@
 Here, even at interannual timescales, the chaotic variance dominates over most of the band of elevated EKE in the Southern Ocean. 
-Subpanels (b) and (c) confirm the predominance of intrinsic eddy variability at this scale, highlighting that at small scales we can place little reliability on the results from an individual ensemble member, or a single observation.
+Subpanels (b) and (c) confirm the predominance of intrinsic eddy variability at this scale, highlighting that at small ($\sim 4^\circ$) scales we can place little reliability on the results from an individual ensemble member, or from actual observations.
 
@@
 When averaged over larger regions, the fraction of intrinsic variance can be smaller than shown in Fig.~\ref{Fig:6}.
-For example, in the Southeast Indian Ocean, in the lee of the Kerguelen Plateau, a strong and rapid response of EKE to the local wind stress can be observed.
-On the other hand, slower but significant responses in EKE are found in the Southwest Pacific Ocean, near Campbell Plateau (Fig.~\ref{Fig:3}).
+For example, in the Southeast Indian Ocean, in the lee of the Kerguelen Plateau, a strong and rapid response of EKE to the local wind stress can be observed (Fig.~\ref{Fig:3}b,c).
+On the other hand, slower but significant responses in EKE are found in the Southwest Pacific Ocean, near Campbell Plateau (Fig.~\ref{Fig:3}c,d).
 Both of these regions are locations where topography acts to sharpen and energise fronts.
@@
 Currents with a non-zonal component are more susceptible to baroclinic instability which thus produces a delayed amplification of the EKE response.
-This mechanism describes a positive feedback between the eddy field and the mean currents which acts to enhance EKE over longer timescales.
+This second mechanism describes a positive feedback between the eddy field and the mean currents which acts to enhance EKE over longer timescales.
 
-The ensemble approach thus leads to the conclusion that eddy processes in the Southern Ocean include a large component of chaotic variability, even when averaged over a large spatial area and up to interannual time scales.
+The ensemble approach thus leads to the conclusion that changes in eddy activity in the Southern Ocean have a strong random character, even when averaged over a large spatial area and up to interannual time scales.
 This result argues for caution in interpreting observations of Southern Ocean eddies, which are necessarily based on a single, short realisation of the natural world.
@@
 \acknowledgments
-This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), which is supported by the Australian Government.
-AMH is gratefully to the MEOM team at ICE, Universit{\'e} Grenoble Alpes, who supported his sabbatical and which led to this work. 
+AMH is gratefully to the MEOM team at IGE, Universit{\'e} Grenoble Alpes, who supported his sabbatical and which led to this work. 
 The results of this research have been achieved using the PRACE Research Infrastructure resource CURIE based in France at TGCC. 
@@
 PIRATE has been funded by CNES through the Ocean Surface Topography Science Team (OST-ST). 
-WKD was funded by ANR-18-MPGA-0002 and NSF grants oce-182956 and oce-2023585.
-{\color{red}The model output used in this study can be downloaded from the Zenodo repository at doi:XXX.XXX.XXX.}
+WKD was funded by ANR-18-MPGA-0002 and NSF grants OCE-182956 and OCE-2023585.
+NCC was funded by the Australian Research Council DECRA Fellowship DE210100749.
+This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), which is supported by the Australian Government.
+
+The model output used in this study can be downloaded from the Zenodo repository at doi: 10.5281/zenodo.5835168.
 The full OCCIPUT model dataset is available on request (\href{mailto:Thierry.Penduff@cnrs.fr}{Thierry.Penduff@cnrs.fr}).

### 2022-04-16 revised_paper/ResponseToReviewers.tex
starting revisions

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{color}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Brief Article}
\author{The Author}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
%\maketitle

We would like to convey our thanks to both reviewers for the constructive and positive reviews of our paper. 
In the following we have addressed each of the reviewers' comments -- with their comments in blue and our response in plain text.

\section*{Response to Reviewer 1}

{\color{blue} This study uses an ensemble of 50 simulations from an eddy-permitting ocean model to investigate the relative importance of forced (coherent) and intrinsic (chaotic) eddy responses. The simulations use the same wind forcing but differ from each other by adding a stochastic perturbation over 1960. The authors define the forced EKE as the ensemble mean EKE from the 50 simulations, and the chaotic EKE as the difference between each simulation and the ensemble mean. The authors find that the Southern Ocean eddy field is dominated by intrinsic processes instead of forced processes. In addition, the authors identified two timescales on which the wind stress and the forced eddy field are linked.

Overall, the question is important, the approach is creative, the findings are significant, and the presentation is high quality. I think the paper is certainly publishable in JGR. I only have a few minor comments and questions, which I hope the authors can clarify before my recommendation of acceptance.\\}

\noindent Our thanks to the reviewer for their positive assessment. 
We have responded in detail to each of the reviewer's comments below.

\subsection*{\color{blue}Details:}

{\color{blue} 
\begin{description}
\item[ Line 84: ] ``the Southern Ocean", missing words like EKE or eddy field?\\
{\color{black}  We agree and have changed to read ``Southern Ocean EKE'' }

\item[ Lines 140-141:] ``the member's global mean sea level anomaly", is this a single value or a time series? If this is a value, it's more likely to shift each ensemble member's sea surface height with a different value. But it wouldn't affect the sea level anomaly time series at each grid point. \\
{\color{black} This statement refers to a timeseries of the globally averaged sea level anomaly. We have clarified this statement to read:\\
 ``For each ensemble member, and at every time step, the member's global mean sea level anomaly is subtracted at every grid point  \ldots" }

\item[Lines 158-162:] The authors mention that the seasonal EKE variation dominates the statistics. To look at the forced response or the correlation between ensemble-mean EKE and wind stress, they deseasonalize the EKE time series. There is some missing information about how they smooth wind stress, the same as the deseasonalized EKE? Also, maybe some general information about the wind stress can be provided in the method section.\\
{\color{black} Yes, the seasonal cycle is also removed from the wind stress. We have added, on line 189, the caveat that wind stress ``\ldots has been deseasonalised in a similar way to $E_i$ \ldots". }

\item[Lines 176-179:] ``Analogously, the intrinsic variance emerges from the variance, indicating the spread of each member from the ensemble mean"; I feel this sentence is not accurate. Normally the closest meaning of spread is the standard deviation. I would suggest the author rephrase it like this: ``For each time step, the intrinsic variance emerges from the variance of EKE difference between ensemble mean and each member of the 50 simulations.'' \\
{\color{black} Amended as suggested. }

\item[Lines 185-186:] between the EKE (...) AND WHAT? Missing words?\\
{\color{black} We have added ``and its forcing''. }

\item[Line 201:] show $\to$ shows\\
{\color{black} Amended. }

\item[Figure 1:] The ensemble mean EKE pattern is consistent with the mean EKE pattern from satellite altimetry. Since this study focuses more on the EKE variabilities, it would be helpful showing to what extent the averaged EKE anomaly time series (group members and ensemble mean) agree with the EKE anomaly time series from satellite altimetry. Also, please label the longitude, latitude, and the major topographic features. \\
{\color{black}  }

\item[Line 231:] add citations (e.g., Meredith \& Hogg, 2006; Hogg et al., 2015) \\
{\color{black} Added as suggested }

\item[Line 231:] As found in this paper, the significance of the wind-leading lag correlation is affected by the size and location of the research area. To compare with previous studies, such as Meredith \& Hogg (2006), Hogg et al., (2015), doesn't it make more sense to use the same average boxes? \\
{\color{black} This line actually refers to the circumpolar average, and so provides a direct comparison, as the reviewer suggests.  
For the later parts of the paper where we examine sub-domains, we considered replicating the original Meredith \& Hogg (2006) boxes, but we found that the ensemble approach allows us to refine those boxes to be considerably smaller, while still obtaining meaningful results.
We could happily add an extra figure with the larger Meredith \& Hogg (2006) boxes, but considered this to be of marginal value to the reader.}

\item[Figure 2:] Based on the definition of EKE and wind stress, they should always be positive. To be accurate, I would suggest the authors label them clearly. Same comment for time series plots in figure 3 and figure 4. \\
{\color{black} We agree more information is needed here and  have noted in the caption of figure 2 that the timeseries shows ``ensemble mean {\color{red}EKE anomaly} (red) along with wind stress {\color{red}anomaly} \ldots'', where red text has been added. 
The captions for figures 3 and 4 have been similarly clarified.}

\item[Line 239-240:] What's the T value for the 4 months and 30 months peaks? \\
{\color{black}  }

\item[Line 241:] dominanent $\to$ dominant?\\
{\color{black} Corrected, thankyou. }

\item[Line 274:] Southeast $\to$ Southwest\\
{\color{black} Amended. }

\item[Figure 3:] (a) A colorbar could be useful. Also, when you define the 3 boxes, do you use rectangular boxes like (70$^\circ$E-120$^\circ$E, 45$^\circ$S-60$^\circ$S)? The boxes shown in Figure 3(a) are more like irregular polygons. It will be better if the author can describe how those boxes are defined. \\
{\color{black}  }

\item[Line 276:] Do the envelopes in Figures 2(b), 3(d), and 4(d) indicate significant lag correlations? If so, it's not accurate to state "no significant response" here.\\
{\color{black} We agree with the reviewer here and have removed that statement. }

\item[Figure 4:] (a) Same comments as Figure 3 (a). In figure 4(b), the caption of the right axis is missing. \\
{\color{black}  }

\item[Figure 5:] Why is there a small missing longitudinal sector?\\
{\color{black} The small missing sector is a consequence of coarsening onto the larger grid, meaning that periodic fields are poorly mapped onto the circumpolar projection. }

\end{description}
}

\newpage

\section*{Response to Reviewer 2}

{\color{blue} I would like to begin by apologising to the authors for the delay in my review. Unfortunately, it became due at a time where there were multiple demands upon my time and I did a poor job at managing them. I apologise for the delay to the publication process this has caused.

The paper is an interesting and well written look at how variability in the Southern Ocean. It is presented very clearly, despite the complex nature of mesoscale eddy dynamics and the challenges of analysing what I am sure is a very large dataset. The analysis uses some simple statistical metrics to break the variability into a fraction that is due to intrinsic variability and that due to direct forcing from wind stress. The conclusions are well supported by the data and the figures are extremely clear. It is very easy for me to recommend publication as-is.

I have noted a few very minor things below, which the authors may wish to address at the proof stage.\\}

\noindent Our thanks to the reviewer for their suggestions; see the following for our responses.

{\color{blue} 
\begin{description}
\item[line 66;] dynamics, plural or singular? I'm not sure.\\
{\color{black} Singular -- amended to ``dynamic''. }

\item[line 128;] is this spinup forced by DFS5.2 as well?\\
{\color{black} Yes -- we have added that information to the revised manuscript. }

\item[line 139;] daily or day?\\
{\color{black} Altered to ``day''.}

\item[line 158;] is the subsampling achieved by selecting a single mean or by averaging them into monthly equivalents?\\
{\color{black} We don't quite understand the point that the reviewer is getting at here, but have clarified by adding the phrase ``\ldots  through weighted averages". }

\item[line 161;] removing THE mean seasonal cycle\\
{\color{black} Amended as suggested }

\item[line 197;] is the $r$ in Eq. (10) the correlation coefficient at the current lag, rather than at a specific lag?\\
{\color{black} Yes, $r$ is as defined 9 lines earlier. }

\item[line 214;] ensemble member AS thin grey lines\\
{\color{black} Amended as suggested. }

\item[line 241;] dominanent to dominant?\\
{\color{black} Corrected. }

\item[line 372;] a reference would be helpful for anyone unfamiliar with the literature.\\
{\color{black} Reference to Arbic \& Flierl (2004) added. }

\end{description}
}

\end{document}

### 2022-04-16 revised_paper/revised.tex
starting revisions

--- 2022-01-13 paper/main.tex
@@
 For example, the eddy saturation hypothesis \citep{Hallberg2006, Meredith-Hogg-2006, Munday2013, Constantinou2019} suggests that the role of eddies in facilitating vertical momentum transport acts to limit the response of ACC transport to changing winds.
-A similar dynamics, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
+A similar dynamic, known as eddy compensation, describes the role of eddies in moderating the effect of wind-driven change on the Southern Ocean overturning circulation \citep{Morrison2013a}.
 Therefore, the response of mesoscale transient motion in the Southern Ocean is likely important to characterising the dynamics of this region.
@@
 Idealised model studies over a wide range of parameter space \citep{Sinha2016} have highlighted that the timescale of the perturbation is critical in determining the EKE response, with shorter perturbations having a faster, Ekman-related response.
-Thus, current knowledge suggests that there is a relationship between wind forcing and the Southern Ocean, but that the nature of this relationship needs to be clarified.
+Thus, current knowledge suggests that there is a relationship between wind forcing and Southern Ocean EKE, but that the nature of this relationship needs to be clarified.
 
@@
 \begin{enumerate}
-\item The 50 ensemble members are initialized in 1960 from a single-member 21-year spinup;
+\item The 50 ensemble members are initialized in 1960 from a single-member 21-year spinup using the Drakkar Forcing Set DFS5.2 \citep{Dussin-etal-2016};
 \item The ensemble spread is seeded by activating a stochastic perturbation \citep{Brankart-etal-2015} over one year (1960), after which the perturbation is terminated;
@@
 \subsection{Estimating geostrophic eddy velocity}
-For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member). 
-For each ensemble member, the member's global mean sea level anomaly is subtracted from all grid points at every time step to correct for spurious terms introduced by the use of the Boussinesq approximation \citep{Greatbatch1994}.
+For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-day average (where $i$ represents the ensemble member). 
+For each ensemble member, and at every time step, the member's global mean sea level anomaly is subtracted at every grid point to correct for spurious terms introduced by the use of the Boussinesq approximation \citep{Greatbatch1994}.
 The model drift, which is potentially nonlinear, is then corrected for by detrending using a LOWESS filter \citep{Cleveland1979} in combination with a 5th-order spline; full details of this preprocessing may be found in \cite{Close2020}.
@@
 \end{linenomath*}
-and subsampled at monthly temporal resolution.
-It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2021}.
-To look at the forced response, we therefore deseasonalise $E_i$, by removing mean seasonal cycle.
+and subsampled at monthly temporal resolution through weighted averages.
+It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2022}.
+To look at the forced response, we therefore deseasonalise $E_i$, by removing the mean seasonal cycle.
 We then proceed to compute ensemble statistics from this deseasonalised EKE.
@@
 which represents the variance of the forced eddy response.
-Analogously, the intrinsic variance emerges from the variance,
+For each time step, the intrinsic variance emerges from the variance of the EKE difference between ensemble mean and each member of the 50 simulations,
 \begin{linenomath*}
 \begin{equation}
-\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i^*(t)^2,
+\epsilon^2(t) = \frac{1}{N} \sum_{i=1}^N E_i^*(t)^2.
 \end{equation}
 \end{linenomath*}
-indicating the spread of each member from the ensemble mean.
 The fraction of intrinsic variance is then computed as the ratio of the intrinsic variance to the total variance,
@@
 
-To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
-Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $|\tau|$ (which is identical for all ensemble members) and EKE.
+To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) and its forcing, we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
+Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $|\tau|$ (which is identical for all ensemble members and has been deseasonalised in a similar way to $E_i$) and EKE.
 For each correlation we evaluate the statistical significance of the correlation \citep[following, e.g.][]{Santer2000}.
@@
 The intensity of the Southern Ocean eddy field is not uniform.
-A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) show the occurrence of strong eddies which appear in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
+A snapshot of eddy kinetic energy from the model used here (Fig.~\ref{Fig:1}a) shows the occurrence of strong eddies which appear in the lee of subsurface topography and at the outlet from western boundary currents such as the Agulhas retroflection and Malvinas current.
 The same patterns are evident in the ensemble and temporal mean of the EKE ($\overline{\langle E \rangle}$; Fig.~\ref{Fig:1}b), although the signal of individual eddies is no longer apparent.
@@
 
-For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member in thin grey lines in Fig.~\ref{Fig:2}(a).
+For each of the 50 members of the OCCIPUT ensemble we take the EKE averaged over the entire Southern Ocean (40$^\circ$-60$^\circ$S), and plot the deseasonalised EKE anomalies from each ensemble member as thin grey lines in Fig.~\ref{Fig:2}(a).
 This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
@@
 \caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S).
-(a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean (red) along with wind stress (black); and (b) Time-lagged correlation between wind stress and EKE for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
+(a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean EKE anomaly (red) along with wind stress anomaly (black); and (b) Time-lagged correlation between wind stress and EKE for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
 \label{Fig:2}
@@
 Previous studies have inferred that there is a strong contribution of wind stress forcing upon EKE, and we therefore compare the forced variability with the variations in wind stress averaged over the same circumpolar belt (black line in Fig.~\ref{Fig:2}a).
-This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results.
+This comparison suggests a relationship in which wind stress leads variations in EKE, consistent with previously published results \citep{Meredith-Hogg-2006,Hogg2015}.
 However, the time-lagged correlations between wind stress and EKE implies that this relationship is complex. 
@@
 The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
-Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model, overprinted by a dominanent and complex influence of chaotic variability.
+Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model, overprinted by a dominant and complex influence of chaotic variability.
 
@@
 \caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
-(a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+(a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southeast Indian Ocean showing ensemble mean EKE anomaly in cyan, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; (c) Lagged correlation of ensemble mean EKE anomaly with wind stress anomaly in each of the three regions; (d) Regional analysis of the Southwest Pacific Ocean showing ensemble mean EKE anomaly in red, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; and (e) Regional analysis of the South Atlantic Ocean showing ensemble mean EKE anomaly in orange, individual ensemble members EKE anomaly in grey and local wind stress averaged anomaly over the region in black.
 The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
@@
 
-In the Southeast Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation clearly differs.
-Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer; there is no significant response to wind stress variations which occur at sub-annual scales (Fig.~\ref{Fig:3}d).
+In the Southwest Pacific Ocean (red box in Fig.~\ref{Fig:3}a) the situation clearly differs.
+Here, the intrinsic variance fraction is larger than in the Southeast Indian Ocean ($R_i=0.78$) and the timescale of the variability is much longer (Fig.~\ref{Fig:3}d).
 The maximum values in the lag correlation occur over a broad band from 9-24 months in this region, without a single clear peak.
@@
 \caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean.
-(a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black.
+(a) Map showing ensemble mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Central South Pacific Ocean showing ensemble mean EKE anomaly in cyan, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; (c) Lagged correlation of ensemble mean EKE anomaly with wind stress anomaly in each of the three regions; (d) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE anomaly in red, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black; and (e) Regional analysis of the Southwest Indian  Ocean showing ensemble mean EKE anomaly in orange, individual ensemble members EKE anomaly in grey and local wind stress anomaly averaged over the region in black.
 The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
@@
 \includegraphics[width=\hsize]{Figure7}
-\caption{(a) The intrinsic variance fraction, $R_i$, averaged onto a  4$^\circ \times$4$^\circ$ grid and with a 12-month rolling mean; (b) amplitude of variability due to forced processes and (c) amplitude of variability due to intrinsic processes.
+\caption{(a) The interannual intrinsic variance fraction, $R_i$, averaged onto a  4$^\circ \times$4$^\circ$ grid and with a 12-month rolling mean; (b) amplitude of interannual variability due to forced processes and (c) amplitude of interannual EKE variability due to intrinsic processes.
  }
@@
 The stronger eddy field acts to increase the vertical momentum transfer which enables topography to steer the current and thereby increase the meridional component of the mean flow. 
-Currents with a non-zonal component are more susceptible to baroclinic instability which thus produces a delayed amplification of the EKE response.
+Currents with a non-zonal component are more susceptible to baroclinic instability \citep[e.g.][]{Arbic2004} which thus produces a delayed amplification of the EKE response.
 This second mechanism describes a positive feedback between the eddy field and the mean currents which acts to enhance EKE over longer timescales.

### 2022-04-17 revised_paper/ResponseToReviewers.tex
tinkering with text and responses

@@
 \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
-\geometry{a4paper}                   % ... or a4paper or a5paper or ... 
+\geometry{a4paper,
+  top=25mm,
+  bottom=30mm,
+  left=25mm,
+  right=25mm}                   % ... or a4paper or a5paper or ... 
 %\geometry{landscape}                % Activate for for rotated page geometry
@@
 
-We would like to convey our thanks to both reviewers for the constructive and positive reviews of our paper. 
+\noindent We would like to convey our thanks to both reviewers for the constructive and positive reviews of our paper. 
 In the following we have addressed each of the reviewers' comments -- with their comments in blue and our response in plain text.
@@
 \item[ Line 84: ] ``the Southern Ocean", missing words like EKE or eddy field?\\
-{\color{black}  We agree and have changed to read ``Southern Ocean EKE'' }
+{\color{black}  We agree and have changed to read ``Southern Ocean EKE''.}
 
@@
 Also, maybe some general information about the wind stress can be provided in the method section.\\
-{\color{black} Yes, the seasonal cycle is also removed from the wind stress.
-We have added, on line 189, the caveat that wind stress ``\ldots has been deseasonalised in a similar way to $E_i$ \ldots".
-}
+{\color{black} Yes, the seasonal cycle is also removed from the wind stress. We have added, on line 189, the caveat that wind stress ``\ldots has been deseasonalised similarly to $E_i$ \ldots". }
 
@@
 \\
-{\color{black}  }
+{\color{black}  We have added latitude and longitude to Figure 1 as suggested (and made minor improvements to the plot).
+We tested labelling major topographic features, but there are many features that could be labelled and it quickly gets messy, so opted to leave the plot as is.
+
+Including the observed EKE trend is a good idea, and we have added this data to Figure~2(a) (green line), using EKE data calculated from Mart\`inez-Moreno et al. (2021).
+This new plot shows that the observed EKE is indistinguishable from the individual ensemble members, but differs from the ensemble mean.}
 
@@
 \\
-{\color{black} We agree more information is needed here and  have noted in the caption of figure 2 that the timeseries shows ``ensemble mean {\color{red}EKE anomaly} (red) along with wind stress {\color{red}anomaly} \ldots'', where red text has been added.
+{\color{black} We agree more information is needed here and have noted in the subtitle of figure 2(a) and the caption of figure 2 that the timeseries shows ``ensemble mean {\color{red}EKE anomaly} (red) along with wind stress {\color{red}anomaly} \ldots'', where red text has been added.
 The captions for figures 3 and 4 have been similarly clarified.}
@@
 \item[Line 239-240:] What's the T value for the 4 months and 30 months peaks? \\
-{\color{black}  }
+{\color{black} The T-values in this case are 5.9 and 3.5 respectively. 
+These values have been added to the manuscript as suggested.  }
 
@@
 \\
-{\color{black}  }
+{\color{black}  We have added a colorbar as suggested.
+Regarding the irregular polygons -- yes, the boxes are long lines of latitude, but we were a little lazy in plotting these on the map projection.
+These boxes have now been fixed to follow latitude lines.
+}
 

### 2022-04-17 revised_paper/revised.tex
tinkering with text and responses

@@
 It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2022}.
-To look at the forced response, we therefore deseasonalise $E_i$, by removing the mean seasonal cycle.
+To look at the forced response, we therefore deseasonalise $E_i$, by removing the climatological mean; we eliminate noise on the monthly timescale by filtering with a 4-month rolling mean.
 We then proceed to compute ensemble statistics from this deseasonalised EKE.
@@
 To examine the relationship between the EKE (of either the ensemble mean, or from individual ensemble members) and its forcing, we are guided by previous work which emphasises the role of wind stress in governing the eddy variability at different timescales \citep[e.g.][]{Hogg2015, Sinha2016}.
-Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $|\tau|$ (which is identical for all ensemble members and has been deseasonalised in a similar way to $E_i$) and EKE.
+Thus, we look at the correlation coefficient, $r$, at a range of lags between the wind stress $|\tau|$ (which is identical for all ensemble members and has been deseasonalised similarly to $E_i$) and EKE.
 For each correlation we evaluate the statistical significance of the correlation \citep[following, e.g.][]{Santer2000}.
@@
 This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
+The observed EKE anomaly \citep[calculated using data from ][ and filtered using the same methods as model output]{Martinez-Moreno2022} indicates that observations are indistinguishable from the individual ensemble members.
 Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
@@
 \caption{Eddy kinetic energy statistics over the Southern Ocean (40$^\circ$S--60$^\circ$S).
-(a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean EKE anomaly (red) along with wind stress anomaly (black); and (b) Time-lagged correlation between wind stress and EKE for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
+(a) Spatially averaged deseasonalised EKE anomaly (relative to climatology) for individual ensemble members (grey) and the ensemble mean EKE anomaly (red) and observed EKE anomaly from the satellite era \citep[green line; calculated from ][]{Martinez-Moreno2022}, along with wind stress anomaly (black); and (b) Time-lagged correlation between wind stress and EKE for the ensemble mean (red) and individual ensemble  members (grey) -- with two individual ensemble members highlighted in magenta and orange.}
 \label{Fig:2}
@@
 These isolated examples highlight the differing behaviour of each ensemble member. 
-The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4 months and a second significant peak at $\sim$30 months.
+The ensemble mean (red line in Fig~\ref{Fig:2}b) includes a significant correlation at $\sim$4~months ($T=5.9$) and a second significant peak at $\sim$30~months ($T=3.5$).
 Thus, two distinct timescales of response of the Southern Ocean eddy field to wind stress are present in this model, overprinted by a dominant and complex influence of chaotic variability.

### 2022-04-17 revised_paper/ResponseToReviewers.tex
revising

@@
 
+\section*{Response to Reviewers}
 \noindent We would like to convey our thanks to both reviewers for the constructive and positive reviews of our paper. 
-In the following we have addressed each of the reviewers' comments -- with their comments in blue and our response in plain text.
+In the following pages we have addressed each of the reviewers' comments -- with their comments in blue and our response in plain text.
 
-\section*{Response to Reviewer 1}
+\subsection*{Response to Reviewer 1}
 
@@
 \noindent Our thanks to the reviewer for their positive assessment. 
-We have responded in detail to each of the reviewer's comments below.
-
-\subsection*{\color{blue}Details:}
+We have responded in detail to each of the reviewer's specific comments below.
 
@@
 Also, maybe some general information about the wind stress can be provided in the method section.\\
-{\color{black} Yes, the seasonal cycle is also removed from the wind stress. We have added, on line 189, the caveat that wind stress ``\ldots has been deseasonalised similarly to $E_i$ \ldots". }
+{\color{black} Yes, the seasonal cycle is also removed from the wind stress.
+We have added, on line 193 of the revised manuscript, the caveat that wind stress ``\ldots has been deseasonalised similarly to $E_i$ \ldots".
+}
 
@@
 {\color{black}  We have added latitude and longitude to Figure 1 as suggested (and made minor improvements to the plot).
-We tested labelling major topographic features, but there are many features that could be labelled and it quickly gets messy, so opted to leave the plot as is.
+We tested labelling major topographic features, but there are many features that could be labelled and it quickly gets messy, so we opted to leave the plot without labelling features.
 
-Including the observed EKE trend is a good idea, and we have added this data to Figure~2(a) (green line), using EKE data calculated from Mart\`inez-Moreno et al. (2021).
+Including the observed EKE trend is a good idea, and we have added this data to Figure~2(a) (green line), using EKE data calculated from Mart\`inez-Moreno et al. (2022).
 This new plot shows that the observed EKE is indistinguishable from the individual ensemble members, but differs from the ensemble mean.}
@@
 For the later parts of the paper where we examine sub-domains, we considered replicating the original Meredith \& Hogg (2006) boxes, but we found that the ensemble approach allows us to refine those boxes to be considerably smaller, while still obtaining meaningful results.
-We could happily add an extra figure with the larger Meredith \& Hogg (2006) boxes, but considered this to be of marginal value to the reader.}
+We could happily add an extra figure with the larger Meredith \& Hogg (2006) boxes, but consider this additional figure to be of marginal value to the reader.}
 
@@
 \item[Figure 4:] (a) Same comments as Figure 3 (a). In figure 4(b), the caption of the right axis is missing. \\
-{\color{black}  }
+{\color{black}  Figure 4 now includes a colorbar and improved box boundaries as per Figure 3.
+The missing axis label has been reinstated.}
 
 \item[Figure 5:] Why is there a small missing longitudinal sector?\\
-{\color{black} The small missing sector is a consequence of coarsening onto the larger grid, meaning that periodic fields are poorly mapped onto the circumpolar projection. }
+{\color{black} The small missing sector was a consequence of a particular choice of option when coarsening onto the larger grid, meaning that periodic fields were poorly mapped onto the circumpolar projection.
+We have now used a better option for coarsening and the field now covers the full 360$^\circ$ of longitudes.
+
+We have also fixed the irregular polygon shapes of the boxes on Figure 5, as per Figures 3 and 4.}
 
@@
 
-\section*{Response to Reviewer 2}
+\subsection*{Response to Reviewer 2}
 
@@
 \item[line 161;] removing THE mean seasonal cycle\\
-{\color{black} Amended as suggested }
+{\color{black} Amended as suggested.}
 
 \item[line 197;] is the $r$ in Eq. (10) the correlation coefficient at the current lag, rather than at a specific lag?\\
-{\color{black} Yes, $r$ is as defined 9 lines earlier. }
+{\color{black} Yes, $r$ is the coefficient at a given lag, as defined 9 lines earlier. }
 

### 2022-04-19 revised_paper/ResponseToReviewers.tex
minor edits following comments from Bill

@@
 \item[Line 241:] dominanent $\to$ dominant?\\
-{\color{black} Corrected, thankyou. }
+{\color{black} Corrected, thank you. }
 
@@
 \item[line 158;] is the subsampling achieved by selecting a single mean or by averaging them into monthly equivalents?\\
-{\color{black} We don't quite understand the point that the reviewer is getting at here, but have clarified by adding the phrase ``\ldots  through weighted averages". }
+{\color{black} We don't quite understand the point that the reviewer is getting at here, but have clarified by adding the phrase ``\ldots   (by taking the weighted average over each month)". }
 

### 2022-04-19 revised_paper/revised.tex
minor edits following comments from Bill

@@
 The Southern Ocean region is also a place where mid- and high-latitude ventilation of the oceans occurs, leading to carbon and heat uptake and controlling deep ocean stratification \citep{Rousselet2021, Morrison2022}.
-However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that the dynamics of this region (with the aim of predicting future responses to climate change) need to be urgently constrained.
+However, the Southern Ocean is also poorly observed (compared with other ocean basins) and its unique properties mean that improved understanding of the dynamics of this region will important implications (with the aim of predicting future responses to climate change).
 
@@
 \end{linenomath*}
-and subsampled at monthly temporal resolution through weighted averages.
+and subsampled at monthly temporal resolution (by taking the weighted average over each month).
 It is notable that $E_i$ contains a large component of seasonal variation which dominates the statistics \citep{Martinez-Moreno2022}.

### 2022-04-20 revised_paper/revised.tex
final resubmitted version

@@
 \documentclass[linenumbers]{agujournal2019}
-
-\graphicspath{ {figures/} }
-%\usepackage{lineno,layouts,microtype}
 
@@
 This plot highlights the considerable spread in EKE, even when averaged over the full circumpolar belt; in other words, there is a significant component of chaotic (intrinsic) variability in the Southern Ocean eddy field.
-The observed EKE anomaly \citep[calculated using data from ][ and filtered using the same methods as model output]{Martinez-Moreno2022} indicates that observations are indistinguishable from the individual ensemble members.
+The observed EKE anomaly \citep[calculated using data from ][ and filtered using the same methods as model output]{Martinez-Moreno2022} indicates that observations are indistinguishable from the individual ensemble members (with the exception of a short period of anomalously low EKE in the early part of the satellite record).
 Nonetheless, when averaged over all ensemble members (red line in Fig.~\ref{Fig:2}a) the existence of a coherent (forced) component of eddy variability is revealed.
-Averaged over this wide region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate the variability in the eddy field averaged over the basin.
+Averaged over this broad region the fraction, $R_i$, of intrinsic variance is 0.82, confirming the visual impression that intrinsic processes dominate the variability in the eddy field averaged over the basin.
 
